---
title: "2018 Resource Pulse Microcolony Analysis - Round 2"
subtitle: "Data cleanup and summarization"
date: "2/1/2018"
output: html_notebook
---

### Import packages 
```{r}
library(tidyverse)
library(lubridate)
```

### Import data
```{r}
mc2.df <- read_csv("D2018_MicroCol_Round2.csv",
                   skip = 1,
                   col_names = c(
                     "id",
                     "date",
                     "time",
                     "initials",
                     "temp",
                     "humidity",
                     "activity",
                     "mc_mass",
                     "n_drones",
                     "n_new_drones",
                     "n_worker_deaths",
                     "brood",
                     "workers_replaced",
                     "drones_removed",
                     "p_mass_rm",
                     "n_mass_rm",
                     "p_mass_fd",
                     "n_mass_fd"),
                     na = c(" ", "N/A", "x")
                   )
mc2.df$date <- mdy(mc2.df$date)

mc2.end.df <- read_csv("./D2018_MicroCol_Round2_BroodMass.csv",
                       skip = 1,
                       col_names = c("id",
                                     "end_mass_comb",
                                     "mass_mc_box"))
mc2.df$treatment <- ifelse(
  mc2.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc2.df$id < 3 & mc2.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc2.df$id < 4 & mc2.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc2.end.df$treatment <- ifelse(
  mc2.end.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc2.end.df$id < 3 & mc2.end.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc2.end.df$id < 4 & mc2.end.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc2.df <- mc2.df %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(fd_day = row_number())
mc2.df$id <- as.factor(mc2.df$id)
```

### Calculate food consumption/colony growth
#### Pull relevant vars
```{r}
mc2.feed.df <- tibble(id = mc2.df$id, 
                      date = mc2.df$date,
                      mc_mass = mc2.df$mc_mass,
                      p_mass_rm = mc2.df$p_mass_rm,
                      p_mass_fd = mc2.df$p_mass_fd,
                      n_mass_fd = mc2.df$n_mass_fd,
                      n_mass_rm = mc2.df$n_mass_rm,
                      treatment = mc2.df$treatment,
                      fd_day = mc2.df$fd_day)
```

#### Colony initiation mass + pollen added
```{r}
mc2.feed.init <- mc2.feed.df[mc2.feed.df$fd_day == 1, ]
mc2.feed.init$n_mass_rm <- NA
mc2.feed.init$p_mass_fd <- NA
mc2.feed.init$p_mass_fd <- 3.00
mc2.feed.init$fd_day <- 0

mc2.feed.df <- mc2.feed.df %>%
  dplyr::bind_rows(mc2.feed.init) %>%
  dplyr::arrange(id, fd_day)
```

#### Pollen start and stop points, etc.
```{r}
pollen.subtract.r2 <- mc2.feed.df %>%
  dplyr::filter(!is.na(p_mass_rm))
pollen.subtract.r2 <- as.vector(pollen.subtract.r2$p_mass_rm)

mc2.feed.df$p_mass_rm[mc2.feed.df$p_mass_fd == 3] <- 0.0 

start.r2 <- which(!is.na(mc2.feed.df$p_mass_rm))
stop.r2 <- start.r2 - 1 # stop points are 1 behind the start
#start.r2 <- head(start.r2, -1) # trim off last start index
stop.r2 <- tail(stop.r2, -1) # trim off first stop index to correctly align
stop.r2 <- c(stop.r2, nrow(mc2.feed.df))

print(start.r2)
print(stop.r2)
```

#### Calculate total pollen provided/consumed
```{r}
pollen.sum.r2 <- c(rep(0, length(start.r2)))
for (i in 1:length(start.r2)) {
  for (j in start.r2[i]:stop.r2[i]) {
    pollen.sum.r2[i] <- pollen.sum.r2[i] + mc2.feed.df$p_mass_fd[j]
  }
}
print(pollen.sum.r2)
length(pollen.subtract.r2)
length(pollen.sum.r2)

length(pollen.subtract.r2) == length(pollen.sum.r2 - pollen.subtract.r2) #FALSE

psum.rm.r2 <- seq(6, length(pollen.sum.r2), by = 6) # Index pos. of each 
pollen.sum.r2 <- pollen.sum.r2[-psum.rm.r2]
print(pollen.sum.r2)
length(pollen.subtract.r2) == length(pollen.sum.r2)
```

```{r}
pollen.consumed.r2 <- pollen.sum.r2 - pollen.subtract.r2
print(pollen.consumed.r2)
```

##### Add pollen consumed column
```{r}
mc2.feed.df$p_mass_cons <- NA
pcons.index.r2 <- stop.r2[-psum.rm.r2]
mc2.feed.df$p_mass_cons[pcons.index.r2 + 1] <- pollen.consumed.r2
mc2.feed.df$p_mass_cons[which(mc2.feed.df$p_mass_rm == 0)] <- 0.00
```

#### Calculate average daily pollen/nectar consumption
```{r}
mc2.feed.df$p_mass_cons_avg <- NA
fd.days.r2 <- ((stop.r2 - start.r2) + 1)
mc2.feed.df$p_mass_cons_avg[which(!is.na(mc2.feed.df$p_mass_cons))] <-
  mc2.feed.df$p_mass_cons[which(!is.na(mc2.feed.df$p_mass_cons))] / fd.days.r2
mc2.feed.df <- fill(mc2.feed.df, 
                    p_mass_cons_avg, 
                    .direction = "up")
mc2.feed.df$p_mass_cons_avg[mc2.feed.df$p_mass_cons_avg == 0] <- NA
mc2.feed.df$p_mass_cons_avg <- as.numeric(mc2.feed.df$p_mass_cons_avg) # for some 
# reason it was boolean...? 
mc2.feed.df$n_mass_cons <- NA
mc2.feed.df$n_mass_rm <- as.numeric(mc2.feed.df$n_mass_rm)
mc2.feed.df$n_mass_cons <- mc2.feed.df$n_mass_fd - lead(mc2.feed.df$n_mass_rm)
mc2.feed.df$n_mass_cons <- as.numeric(mc2.feed.df$n_mass_cons)
mc2.feed.df$treatment <- as.factor(mc2.feed.df$treatment)
```

### Calculate true mass 
```{r}
mc2.feed.df <- mc2.feed.df %>%
  group_by(id) %>%
  mutate(fd_day_count = c(0, rep(seq(3, 1, by = -1), 5), 0))

mc2.feed.df <- mc2.feed.df %>%
  group_by(id) %>%
  mutate(mc_mass_init = mc_mass[fd_day == 0] - 3)
mc2.feed.df <- mc2.feed.df %>%
  ungroup() %>%
  mutate(mc_mass_true = ifelse(
    fd_day_count == 3,
    ((mc_mass - mc_mass_init) + p_mass_cons_avg),
    ifelse(
      fd_day_count == 2,
      (((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) + p_mass_cons_avg),
      ifelse(
        fd_day_count == 1,
        ((((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) - lag(p_mass_fd, n = 2)) + p_mass_cons_avg),
        0
        )
      )
    ))
mc2.feed.df$mc_mass_true[mc2.feed.df$mc_mass_true == 0] <- NA
mc2.feed.df$mc_mass_true[mc2.feed.df$fd_day == 0] <- 0.00
mc2.feed.df$date[mc2.feed.df$mc_mass_true == 0] <- "2018-06-18"
```

#### Calculate avg. mass difference
```{r}
mc2.feed.df <- mc2.feed.df %>%
  mutate(mc_mass_diff = c(NA, diff(mc_mass_true)))
```


### Create time category relative to pulse
```{r}
mc2.feed.df <- mc2.feed.df %>%
  ungroup() %>%
  mutate(pulse_cat = ifelse(
    fd_day <= 3, 
    "b1",
    ifelse(
      fd_day > 3 & fd_day <= 6,
      "p1",
      ifelse(
        fd_day > 6 & fd_day <= 10,
        "a1.b2",
        ifelse(fd_day >10 & fd_day <= 13,
               "p2",
               "a2")
      )
    )
  ))
mc2.feed.df$pulse_cat <- as.factor(mc2.feed.df$pulse_cat)
```
### Drone summary/cleanup
```{r}
mc2.drone.df <- mc2.df %>%
  ungroup() %>%
  group_by(id, treatment) %>%
  summarise(total_drones = sum(n_new_drones, 
                               na.rm = TRUE))
```

### Write cleaned data
```{r}
write_csv(mc2.df, "D2018_microcol_round2_clean.csv")
write_csv(mc2.feed.df, "D2018_microcol_round2_feed_clean.csv")
write_csv(mc2.drone.df, "./D2018_microcol_round3_drone.csv")
```

```{r}
# mc2.df %>%
#   dplyr::group_by(id) %>%
#   dplyr::summarise(total_drones = sum(n_new_drones,
#                                na.rm = TRUE))
```

