---
title: "2018 Resource Pulse Microcolony Analysis - Round 1"
subtitle: Analysis and model construction/selection
date: 11/28/2018
output: html_notebook
---

**Name:** Jeremy Hemberger
**Email:** j.hemberger.wisc@gmail.com
**Institution:** University of Wisconsin - Madison | Department of Entomology

### Import packages 
```{r Import libraries`, include=FALSE}
library(psych)
library(nlme) #lmer can't use temporal corrleation structures
library(car)
library(multcompView)
library(lsmeans)
library(tidyverse)
library(rcompanion)
library(lmtest)
```

### Load in data
```{r}
mc1.df <- read_csv("./D2018_MicroCol_Round1_Clean.csv")
mc1.feed.df <- read_csv("./D2018_MicroCol_Round1_Feed_Clean.csv")
mc1.df$treatment <- factor(mc1.df$treatment)
mc1.feed.df$treatment <- factor(mc1.feed.df$treatment)
```

### Round 1 Analyses
#### RM Anova on mass
##### Temporal correlation structure
```{r}
corr.model = lme(mc_mass_true_intrp ~ treatment + date + treatment*date, 
                 random = ~ 1 | id,
                 data = mc1.feed.df,
                 na.action = na.exclude)

ACF(corr.model) # Lag 1: 0.314
acf(mc1.feed.df$mc_mass_true_intrp)
```

##### Full model
```{r}
model.1 = lme(mc_mass_true_intrp ~ treatment + date + treatment*date, 
              random = ~ 1 | id,
              data = mc1.feed.df,
              correlation = corAR1(form = ~ date | id,
                                   value = 0.31456),
              na.action = na.exclude,
              method = "REML")
Anova(model.1)
```

##### Fixed effects only w/comparison
```{r}
model.1.fixed = gls(mc_mass_true_intrp ~ treatment + date + treatment*date,
                    data = mc1.feed.df,
                    method = "REML",
                    na.action = na.exclude)

anova(model.1, model.1.fixed)
```

##### Null model w/comparison
```{r}
model.null <- lme(mc_mass_true_intrp ~ 1,
                 random = ~ 1 | id,
                 data = mc1.feed.df,
                 na.action = na.exclude)

nagelkerke(model.1, 
           model.null)
```

##### LS Means estimates
```{r}
marginal <- lsmeans(model.1, 
                   ~ treatment:date)

mc1.mass.cld <- cld(marginal,
                    alpha   = 0.05, 
                    Letters = letters,
                    adjust  = "tukey")
mc1.mass.cld
```
```{r}
mc1.mass.cld$.group=gsub(" ", "", mc1.mass.cld$.group)
ggplot(data = mc1.mass.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  geom_text(mapping = aes(y = upper.CL + 0.5),
             color = "white") + 
  ylab("Least square mean microcolony mass") + 
  xlab("Treatment")
```

##### Groupwise estimated means across exp
```{r}
mc1.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  mc_mass_true_intrp ~ treatment + date,
  data = mc1.feed.df,
  conf = 0.95,
  digits = 3,
  traditional = FALSE,
  percentile = TRUE
  )

mc1.gwm.df
```

Plot groupwise means from above
```{r}
pd = position_dodge(0.2)
ggplot(mc1.gwm.df, aes(x = date,
                       y = Mean,
       color = treatment)) +
  geom_errorbar(aes(ymin = Percentile.lower,
                    ymax = Percentile.upper),
                  width = 0.2, 
                  size = 0.7, 
                  position = pd) +
  geom_point(size = 4, 
             position = pd) +
  theme_black() +
  theme(axis.title = element_text(face = "bold")) +
  ylab("Least square mean mass") + 
  xlab("Date")
```

##### Model diagnostics
```{r}
model.1.resid <- residuals(model.1)
plotNormalHistogram(model.1.resid)
plot(residuals(model.1),
     fitted(model.1))
plot(residuals(model.1))
acf(residuals(model.1))
```

#### RM ANOVA on drone production (__may need GLMM due to count data__) 
##### Calculate cumulative drone production
```{r} 
mc1.cumdrone.df <- mc1.df %>%
  ungroup() %>%
  dplyr::filter(id != 2.4) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(fd.day = row_number()) %>%
  dplyr::mutate(csum_drones = cumsum(n_new_drones)) %>%
  dplyr::arrange(id, date)
```

##### Temporal correlation structure
```{r}
corr.model.cdrone = lme(csum_drones ~ treatment + date + treatment*date, 
                        random = ~ 1 | id,
                        data = mc1.cumdrone.df,
                        na.action = na.exclude)

ACF(corr.model.cdrone) # 1st order lag: 0.7508
acf(mc1.cumdrone.df$csum_drones)
```

##### Full model
```{r}
cdrone.model.1 = lme(csum_drones ~ treatment + date + treatment*date, 
                     random = ~ 1 | id,
                     data = mc1.cumdrone.df,
                     correlation = corAR1(form = ~ date | id,
                                          value = 0.751),
                     na.action = na.exclude,
                     method = "REML")
Anova(cdrone.model.1)
```

##### Fixed effects only w/comparison
```{r}
cdrone.model.1.fixed = gls(csum_drones ~ treatment + date + treatment*date,
                           data = mc1.cumdrone.df,
                           method = "REML",
                           na.action = na.exclude)

anova(cdrone.model.1, cdrone.model.1.fixed)
```

##### Null model w/comparison
```{r}
cdrone.model.null <- lme(csum_drones ~ 1,
                         random = ~ 1 | id,
                         data = mc1.cumdrone.df,
                         na.action = na.exclude)

nagelkerke(cdrone.model.1, 
           cdrone.model.null)
```

##### LS Means estimates
```{r}
cdrone.marginal <- lsmeans(cdrone.model.1,  ~ treatment:date)

mc1.drone.cld <- cld(cdrone.marginal,
                     alpha   = 0.05, 
                     Letters = letters,
                     adjust  = "tukey")
mc1.drone.cld
```

```{r}
mc1.drone.cld$.group=gsub(" ", "", mc1.drone.cld$.group)
ggplot(data = mc1.drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 1.5),
             color = "white") + 
  ylab("Least square mean drone production") + 
  xlab("Treatment")
```
##### Groupwise estimated means across exp
```{r}
mc1.drones.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  csum_drones ~ treatment + date,
  data = mc1.cumdrone.df,
  conf = 0.95,
  digits = 3,
  traditional = FALSE,
  percentile = TRUE
  )

mc1.drones.gwm.df
```

Plot groupwise means from above
```{r}
pd = position_dodge(.2)
ggplot(mc1.drones.gwm.df, aes(x = date,
                              y = Mean,
                              color = treatment)) +
  geom_errorbar(aes(ymin = Percentile.lower,
                    ymax = Percentile.upper),
                  width = 0.2, 
                  size = 0.7, 
                  position = pd) +
  geom_point(size = 4, 
             position = pd,
             alpha = 0.75) +
  theme_black() +
  theme(axis.title = element_text(face = "bold")) +
  ylab("Least-square mean cumulative drone production") + 
  xlab("Date of experiment")
```

##### Model diagnostics
```{r}
cdrone.model.1.resid <- residuals(cdrone.model.1)
plotNormalHistogram(cdrone.model.1.resid)
plot(residuals(cdrone.model.1),
     fitted(cdrone.model.1))
plot(cdrone.model.1)
plot(residuals(cdrone.model.1))
acf(residuals(cdrone.model.1))
```

#### ANOVA for total drone production
##### Define & summarize model
```{r} 
mc1.drone.df <- mc1.drone.df %>%
  filter(id != 2.4)
mc1.drone.lm <- lm(total_males ~ treatment,
                   data = mc1.drone.df)
tidy(mc1.drone.lm)
anova(mc1.drone.lm)
```

##### LS means calculation
```{r}
tdrone.marginal <- lsmeans(mc1.drone.lm,  ~ treatment)

tdrone.cld <- cld(tdrone.marginal,
                  alpha   = 0.05, 
                  Letters = letters,
                  adjust  = "tukey")
tdrone.cld
```

##### Plot LS means
```{r}
tdrone.cld$.group=gsub(" ", "", tdrone.cld$.group)
ggplot(data = tdrone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 2),
             color = "white") + 
  ylab("Least square mean drone production") + 
  xlab("Treatment")
```

#### RM ANOVA for drone IT distance
For this, need to average by date in order to avoid issues fitting temporal correlation structure. 
```{r} 
mc1.drone.itmod.df <- mc1.drone.it.df %>%
  ungroup() %>%
  group_by(date, id, treatment) %>%
  dplyr::summarise(mean.it.distance = mean(it.distance))
```

##### Temporal correlation structure
```{r}
it.corr.model = lme(mean.it.distance ~ treatment + date + treatment*date, 
                    random = ~ 1 | id,
                    data = mc1.drone.itmod.df,
                    na.action = na.exclude)

ACF(it.corr.model) # Lag 1: 0.314
acf(mc1.drone.it.df$it.distance)
```

##### Full model
```{r}
it.model.1 = lme(mean.it.distance ~ treatment + date + treatment*date, 
              random = ~ 1 | id,
              data = mc1.drone.itmod.df,
              correlation = corAR1(form = ~ date | id ,
                                   value = 0.137),
              na.action = na.exclude,
              method = "REML")
Anova(it.model.1)
```

##### Fixed effects only w/comparison
```{r}
it.model.1.fixed = gls(mean.it.distance ~ treatment + date + treatment*date,
                       data = mc1.drone.itmod.df,
                       method = "REML",
                       na.action = na.exclude)

anova(it.model.1, it.model.1.fixed)
```

##### Null model w/comparison
```{r}
it.model.null <- lme(mean.it.distance ~ 1,
                    random = ~ 1 | id,
                    data = mc1.drone.itmod.df,
                    na.action = na.exclude)

nagelkerke(it.model.1, it.model.null)
```

##### LS Means estimates
```{r}
it.marginal <- lsmeans(it.model.1, ~ treatment:date)

it.cld <- cld(it.marginal,
              alpha   = 0.05, 
              Letters = letters,
              adjust  = "tukey")
it.cld
```
```{r}
it.cld$.group = gsub(" ", "", it.cld$.group)
ggplot(data = it.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  geom_text(mapping = aes(y = upper.CL + 0.25),
             color = "white") + 
  ylab("Least square mean drone IT distance") + 
  xlab("Treatment") + 
  theme(legend.position = "none")
```

##### Groupwise estimated means across exp
```{r}
mc1.drone.itmod.df$treatment <- as.factor(mc1.drone.itmod.df$treatment)
it.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  mean.it.distance ~ treatment + date,
  data = mc1.drone.itmod.df
  )

it.gwm.df
```

Plot groupwise means from above
```{r}
pd = position_dodge(.2)
ggplot(it.gwm.df, aes(x = date,
                      y = Mean,
                color = treatment)) +
    geom_errorbar(aes(ymin = Trad.lower,
                      ymax = Trad.upper),
                  width = 0.2, 
                  size = 0.7, 
                  position = pd) +
    geom_point(size = 4, 
               position = pd) +
    theme_black() +
    theme(axis.title = element_text(face = "bold")) +
    ylab("Least square mean IT distance") + 
  xlab("Date")
```

##### Model diagnostics
```{r}
it.model.1.resid <- residuals(it.model.1)
plotNormalHistogram(it.model.1.resid)
plot(residuals(it.model.1),
     fitted(it.model.1))
plot(residuals(it.model.1))
acf(residuals(it.model.1))
```
#### ANOVA for mean drone IT distance
##### Define & summarize model
```{r} 
mc1.drone.it.lm <- lm(it.distance ~ treatment,
                      data = mc1.drone.it.df)
tidy(mc1.drone.it.lm)
anova(mc1.drone.it.lm)
```

##### LS means calculation
```{r}
it.drone.marginal <- lsmeans(mc1.drone.it.lm,  ~ treatment)

it.drone.cld <- cld(it.drone.marginal,
                    alpha   = 0.05, 
                    Letters = letters,
                    adjust  = "tukey")
it.drone.cld
```

##### Plot LS means
```{r}
it.drone.cld$.group = gsub(" ", "", it.drone.cld$.group)
ggplot(data = it.drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 0.25),
             color = "white") + 
  ylab("Least square mean drone IT distance") + 
  xlab("Treatment") + 
  theme(legend.position = "none")
```

##### Model diagnostics
```{r} 
plot(mc1.drone.it.lm)
plot(residuals(mc1.drone.it.lm))
```

#### RM ANOVA for drone mass
##### Temporal correlation structure
```{r}
mass.corr.model = lme(avg.individ.mass ~ treatment + date + treatment*date, 
                      random = ~ 1 | id,
                      data = mc1.drone.mass.df,
                      na.action = na.exclude)

ACF(mass.corr.model) # No sigificant temporal autocorrelation.
acf(mc1.drone.mass.df$avg.individ.mass)
```

##### Full model
```{r}
mass.model.1 = lme(avg.individ.mass ~ treatment + date + treatment*date, 
                   random = ~ 1 | id,
                   data = mc1.drone.mass.df,
                   na.action = na.exclude,
                   method = "REML")
Anova(mass.model.1)
summary(mass.model.1)
```

##### Fixed effects only w/comparison
```{r}
mass.model.1.fixed = gls(avg.individ.mass ~ treatment + date + treatment*date,
                         data = mc1.drone.mass.df,
                         method = "REML",
                         na.action = na.exclude)

anova(mass.model.1, mass.model.1.fixed)
```

##### Null model w/comparison
```{r}
mass.model.null <- lme(
  avg.individ.mass ~ 1,
  random = ~ 1 | id,
  data = mc1.drone.mass.df,
  na.action = na.exclude
  )

nagelkerke(mass.model.1, mass.model.null)
```

##### LS Means estimates
```{r}
mass.marginal <- lsmeans(mass.model.1, ~ treatment:date)

mass.cld <- cld(mass.marginal,
                alpha   = 0.05, 
                Letters = letters,
                adjust  = "tukey")
mass.cld
```
```{r}
mass.cld$.group = gsub(" ", "", mass.cld$.group)
ggplot(data = mass.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  geom_text(mapping = aes(y = upper.CL + 0.01),
             color = "white") + 
  ylab("Least square mean drone mass") + 
  xlab("Treatment") + 
  theme(legend.position = "none")
```

##### Groupwise estimated means across exp
```{r}
mass.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  avg.individ.mass ~ treatment + date,
  data = mc1.drone.mass.df
  )

it.gwm.df
```

Plot groupwise means from above
```{r}
pd = position_dodge(.2)
ggplot(mass.gwm.df, aes(x = date,
                      y = Mean,
                color = treatment)) +
    geom_errorbar(aes(ymin = Trad.lower,
                      ymax = Trad.upper),
                  width = 0.2, 
                  size = 0.7, 
                  position = pd) +
    geom_point(size = 4, 
               position = pd) +
    theme_black() +
    theme(axis.title = element_text(face = "bold")) +
    ylab("Least square mean drone mass estimate") + 
  xlab("Date")
```

##### Model diagnostics
```{r}
mass.model.1.resid <- residuals(mass.model.1)
plotNormalHistogram(mass.model.1.resid)
plot(residuals(mass.model.1),
     fitted(mass.model.1))
plot(residuals(mass.model.1))
acf(residuals(mass.model.1))
```
#### ANOVA for mean drone mass
##### Define & summarize model
```{r} 
mc1.drone.mass.lm <- lm(avg.individ.mass ~ treatment,
                         data = mc1.drone.mass.df)
tidy(mc1.drone.mass.lm)
anova(mc1.drone.mass.lm)
```

##### LS means calculation
```{r}
mass.drone.marginal <- lsmeans(mc1.drone.mass.lm,  ~ treatment)

mass.drone.cld <- cld(mass.drone.marginal,
                      alpha   = 0.05, 
                      Letters = letters,
                      adjust  = "tukey")
mass.drone.cld
```

##### Plot LS means
```{r}
mass.drone.cld$.group = gsub(" ", "", mass.drone.cld$.group)
ggplot(data = mass.drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 0.01),
             color = "white") + 
  ylab("Least square mean drone mass") + 
  xlab("Treatment") + 
  theme(legend.position = "none")
```

##### Model diagniostics
```{r} 
plot(mc1.drone.mass.lm)
```
### ANOVA for days to first drone
##### Create data frame
```{r}
mc1.colinit.df <- mc1.df %>%
  dplyr::filter(id != 2.4) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(index_to_drone = min(which(n_new_drones > 0)),
                date_to_drone = date[index_to_drone]) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(id, treatment) %>%
  dplyr::select(id, treatment, date_to_drone) %>%
  dplyr::mutate(days_to_drone = (as.duration(ymd("2018-03-15") %--% date_to_drone) / 86400)) %>%
  dplyr::ungroup()
mc1.colinit.df <- aggregate(. ~ id, 
                            mc1.colinit.df, 
                            FUN = head, 
                            1)
mc1.colinit.df$id <- as.numeric(as.character(mc1.colinit.df$id))
mc1.colinit.df$days_to_drone <- as.numeric(as.character(mc1.colinit.df$days_to_drone))
mc1.colinit.df
``` 
##### Define & summarize model
```{r} 
mc1.colinit.lm <- lm(days_to_drone ~ treatment,
                     data = mc1.colinit.df)
tidy(mc1.colinit.lm)
plot(mc1.colinit.lm)
hist(mc1.colinit.df$days_to_drone)
anova(mc1.colinit.lm)
```

##### LS means calculation
```{r}
mc1.colinit.marginal <- lsmeans(mc1.colinit.lm,  ~ treatment)

mc1.colinit.cld <- cld(mc1.colinit.marginal,
                       alpha   = 0.05, 
                       Letters = letters,
                       adjust  = "tukey")
mc1.colinit.cld
```

##### Plot LS means
```{r}
mc1.colinit.cld$.group = gsub(" ", 
                              "", 
                              mc1.colinit.cld$.group)
ggplot(data = mc1.colinit.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(fill = "indianred1",
           width = 0.5) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "white") + 
  ylab("Least square mean days to drone production") + 
  xlab("Treatment") + 
  theme(legend.position = "none")
```

### RM ANOVA for worker mortality

### ANOVA for total worker mortality 
##### Create data frame
```{r}
mc1.workmort.df <- mc1.df %>%
  dplyr::group_by(id, treatment) %>%
  dplyr::filter(id != 2.4) %>%
  dplyr::summarise(total_worker_death = sum(n_worker_deaths, 
                                            na.rm = TRUE))
mc1.workmort.df
```

##### Define & summarize model
```{r} 
mc1.workmort.lm <- lm(total_worker_death ~ treatment,
                      data = mc1.workmort.df)
tidy(mc1.workmort.lm)
plot(mc1.workmort.lm)
anova(mc1.workmort.lm)
```

##### LS means calculation
```{r}
mc1.workmort.marginal <- lsmeans(mc1.workmort.lm,  ~ treatment)

mc1.workmort.cld <- cld(mc1.workmort.marginal,
                       alpha   = 0.05, 
                       Letters = letters,
                       adjust  = "tukey")
mc1.workmort.cld
```

##### Plot LS means
```{r}
mc1.workmort.cld$.group = gsub(" ", 
                              "", 
                              mc1.workmort.cld$.group)
ggplot(data = mc1.workmort.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(fill = "indianred1",
           width = 0.5) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "white") + 
  ylab("Least square mean worker mortality") + 
  xlab("Treatment") + 
  theme(legend.position = "none")
```
