---
title: "2018 Resource Pulse Microcolony Analysis - Final manuscipt analyses"
subtitle: Analysis and model construction/selection
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_notebook
---

**Name:** Jeremy Hemberger
**Email:** j.hemberger.wisc@gmail.com
**Institution:** University of Wisconsin - Madison | Department of Entomology

# Import packages 
```{r echo = TRUE, results = "hide"}
library(psych)
library(nlme) #lmer can't use temporal corrleation structures
library(car)
library(multcompView)
library(lsmeans)
library(tidyverse)
library(rcompanion)
library(lmtest)
library(gam)
library(gamm4)
library(mgcv)
library(knitr)
library(lubridate)
library(broom)
library(stargazer)
library(jtools)
```

# Load in data
```{r}
mc1.df <- read_csv("./D2018_MicroCol_Round1_Clean.csv")
mc2.df <- read_csv("./D2018_MicroCol_Round2_Clean.csv")
mc3.df <- read_csv("./D2018_microcol_round3_clean.csv")
mc.end.all.df <- read_csv("./microcol_final_endmass.csv")
mc.feed.all.df <- read_csv("./microcol_final_mass.csv")
mc.dronemass.all.df <- read_csv("./microcol_final_dronemass.csv")
mc.dronemass.all.df$trt_total <- as.character(mc.dronemass.all.df$trt_total)

```

# Models and plots
## MASS
### 2-way ANOVA: end mass
##### Model specification
```{r}
endmass.lmm <- lme(end_mass_comb ~ trt_pulse * trt_total + round,
                   random = ~ 1 | id,
                   data = mc.end.all.df,
                   na.action = na.exclude)
endmass.marginal <- lsmeans(endmass.lmm, ~ trt_pulse:trt_total)
endmass.cld <- cld(endmass.marginal,
                   alpha = 0.05,
                   Letters = letters,
                   adjust = "tukey")
endmass.cld$treatment <- c("zone.4", 
                           "zone.1", 
                           "zone.3", 
                           "zone.2")
endmass.eff <- contrast(endmass.marginal,
                        alpha = 0.05,
                        method = "eff",
                        adjust = "tukey")
endmass.pairwise <- contrast(endmass.marginal,
                             alpha = 0.05,
                             method = "pairwise",
                             adjust = "tukey")
summary(endmass.lmm)
anova(endmass.lmm)
endmass.cld
endmass.eff
endmass.pairwise
```

##### Plots
```{r}
endmass.cld$.group=gsub(" ", "", endmass.cld$.group)
ggplot(data = endmass.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 0.5),
             color = "black") + 
  scale_y_continuous(limits = c(0, 10),
                     expand = c(0, 0)) +
  ylab("Least square mean brood mass") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```


### RM ANOVA: mass
##### Model specification
```{r}
mass.rmlmm = lme(mc_mass_true ~ trt_total * trt_pulse * rep + date,
                 random = ~ 1 + treatment | id,
                 data = mc.feed.all.df,
                 na.action = na.exclude)
mass.acf <- ACF(mass.rmlmm)
mass.acf <- mass.acf %>%
  filter(lag == 1) %>%
  select(ACF)
mass.rmlmm.1 = lme(mc_mass_true ~ trt_total * trt_pulse * rep + date, 
                   random = ~ 1 + treatment | id,
                   data = mc.feed.all.df,
                   correlation = corAR1(form = ~ date | id,
                                        value = mass.acf),
                   na.action = na.exclude,
                   method = "REML")
mass.gwm.df <- groupwiseMean(mc_mass_true ~ treatment + fd_day,
                             data = mc.feed.all.df,
                             conf = 0.95,
                             digits = 3)
summary(mass.rmlmm.1)
anova(mass.rmlmm.1)
```

##### Plots
```{r}
mcall.mass.gwm.df %>%
  ungroup() %>%
  filter(fd_day != 0) %>%
  group_by(treatment) %>%
  mutate(Mean = na.approx(Mean, 
                          maxgap = 4,
                          rule = 2)) %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
ggplot(mapping = aes(x = fd_day,
                     y = Mean,
                     group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean mass") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(mcall.mass.gwm.df$fd_day)) + 
  scale_y_continuous(limits = c(0, 10.5))
```

### 2-way ANOVA: period growth rates
##### Model specification
```{r}
mc.all.trtslope.df <- mc.feed.all.df %>%
  group_by(pulse_cat, id) %>%
  do({
    mod = lm(mc_mass_true ~ fd_day, data = .)
    tibble(intercept = coef(mod)[1],
           slope.estimate = coef(mod)[2])
  })
mc.all.trtslope.df$id <- as.character(mc.all.trtslope.df$id)
mc.all.trtslope.df$treatment <- ifelse(
  mc.all.trtslope.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc.all.trtslope.df$id < 3 & mc.all.trtslope.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc.all.trtslope.df$id < 4 & mc.all.trtslope.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc.all.trtslope.df <- mc.all.trtslope.df %>%
  mutate(pulse_cat_int = ifelse(pulse_cat == "b1",
                                1, ifelse(
                                  pulse_cat == "p1",
                                  2, ifelse(
                                    pulse_cat == "a1.b2",
                                    3, ifelse(
                                      pulse_cat == "p2",
                                      4, ifelse(
                                        pulse_cat == "a2", 
                                        5
                                      )
                                    )
                                  )
                                )))
anova.by.period <- function() {
  periods <- unique(mc.all.trtslope.df$pulse_cat)
  df.ls <- list()
  for(i in periods) {
    df <- mc.all.trtslope.df %>%
      filter(pulse_cat == i)
    lmm <- lme(slope.estimate ~ treatment,
               random = ~ 1 | id,
               data = df,
               na.action = na.omit)
    lsm <- lsmeans(lmm, 
                   ~ treatment)
    cld <- cld(lsm,
               alpha = 0.05,
               Letters = letters,
               adjust = "tukey")
    df.ls[[i]] <- cld
  }
  df.end <- bind_rows(df.ls,
                      .id = "pulse_cat")
  assign("mc.all.period.anovas",
         df.end,
         envir = .GlobalEnv)
}
anova.by.period()
mc.all.period.anovas$pulse_cat <- as.factor(mc.all.period.anovas$pulse_cat)
mc.all.period.anovas$pulse_cat <- factor(mc.all.period.anovas$pulse_cat, 
                                         levels = c("b1",
                                                    "p1",
                                                    "a1.b2",
                                                    "p2",
                                                    "a2"))
mc.all.period.anovas$.group=gsub(" ", 
                                 "", 
                                 mc.all.period.anovas$.group)
mc.all.trtslope.df <- mc.all.trtslope.df %>%
  mutate(trt_pulse = ifelse(id >= 3, 
                            "pulse",
                            "constant"),
         trt_total = ifelse(id < 2 | id > 4,
                            "60",
                            "100"))
massrate.lmm <- lme(slope.estimate ~ trt_pulse * trt_total + pulse_cat,
                    random = ~ 1 | id,
                    data = mc.all.trtslope.df)
massrate.marginal <- lsmeans(massrate.lmm,
                             ~ trt_pulse * trt_total)
massrate.eff <- contrast(massrate.marginal,
                         method = "eff",
                         alpha = 0.05,
                         adjust = "tukey")
massrate.pairwise <- contrast(massrate.marginal,
                              method = "pairwise",
                              alpha = 0.05,
                              adjust = "tukey")
massrate.cld <- cld(massrate.marginal,
                    alpha = 0.05,
                    Letters = letters,
                    adjust = "tukey")
massrate.cld$treatment <- c("zone.1", 
                            "zone.3", 
                            "zone.4", 
                            "zone.2")
summary(massrate.lmm)
anova(massrate.lmm)
massrate.eff
massrate.pairwise
massrate.cld
```

##### Plots
```{r}
mc.feed.all.df %>%
  ungroup() %>%
  filter(fd_day != 0) %>%
  ggplot() + 
  geom_point(mapping = aes(x = fd_day,
                           y = mc_mass_true,
                           color = pulse_cat)) + 
  geom_smooth(mapping = aes(x = fd_day,
                            y = mc_mass_true_intrp,
                            color = interaction(pulse_cat, id)),
              method = "lm",
              se = FALSE) + 
  scale_x_continuous(breaks = unique(mc.feed.all.df$fd_day)) + 
  theme_microcol() + 
  facet_grid(vars(treatment)) + 
  theme(legend.position = "none")

massrate.cld$.group=gsub(" ", "", massrate.cld$.group)
massrate.cld %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = treatment,
                       y = lsmean,
                       label = .group)) + 
  geom_hline(yintercept = 0,
             color = "black",
             size = 0.6,
             alpha = 1) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 0.1),
             color = "black") + 
  scale_y_continuous(limits = c(-0.5, 1.5),
                     expand = c(0, 0)) +
  ylab("Least square mean growth rate") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

### RM ANOVA: period growth rates
##### Model specification
```{r}
massgain.rmlmm = lme(slope.estimate ~ trt_total * trt_pulse * pulse_cat_int, 
                           random = ~ 1 + treatment | id,
                           data = mc.all.trtslope.df,
                           na.action = na.exclude)
massgain.acf <- ACF(massgain.rmlmm)
massgain.acf <- massgain.acf %>%
  filter(lag == 1) %>%
  select(ACF)
massgain.rmlmm.1 = lme(slope.estimate ~ trt_total * trt_pulse * pulse_cat_int, 
                       random = ~ 1 + treatment | id,
                       data = mc.all.trtslope.df,
                       correlation = corAR1(form = ~ pulse_cat_int | id,
                                            value = massgain.acf),
                       na.action = na.exclude,
                       method = "REML")
summary(massgain.rmlmm.1)
anova(massgain.rmlmm.1)
mc.all.trtslope.0.df <- mc.feed.all.df %>%
  group_by(pulse_cat, treatment) %>%
  do({
    tidy(lm(mc_mass_true ~ fd_day,
             data = .))
  }) %>%
  filter(term != "(Intercept)")
mc.all.trtslope.0.df
```

##### Plots
```{r}
mc.all.period.anovas %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(label = .group)) +
  geom_hline(yintercept = 0,
             color = "tomato2",
             size = 1,
             alpha = 1) + 
  geom_pointrange(mapping = aes(x = pulse_cat,
                                y = lsmean,
                                ymin = lower.CL,
                                ymax = upper.CL,
                                color = treatment),
                  size = 0.75) +
  geom_line(mapping = aes(x = pulse_cat,
                          y = lsmean,
                          group = treatment,
                          color = treatment),
            size = 1.25,
            alpha = 1) +
  geom_text(mapping = aes(x = pulse_cat,
                          y = upper.CL + 0.1),
             color = "black",
            position = position_dodge2(width = 0.9)) +
  labs(x = "Period relative to food pulse",
       y = "Mean estimated rate of mass gain") + 
  scale_y_continuous(limits = c(-2, 3.5),
                     breaks = seq(-3, 3, by = 1)) + 
  theme_microcol() + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                     name = "Treatment") +
  facet_grid(rows = vars(trt_cat))
```



## DRONES
### 2-way ANOVA: drone production
##### Model specification
```{r}
drones.lmm <- lme(total_drones ~ trt_pulse * trt_total * rep,
                  random = ~ 1 | id,
                  data = mc.drone.all.df,
                  na.action = na.exclude)
drone.marginal <- lsmeans(drones.lmm, ~ trt_pulse * trt_total)
drone.cld <- cld(drone.marginal,
                 alpha = 0.05,
                 Letters = letters,
                 adjust = "tukey")
drone.cld$treatment <- c("zone.1", 
                         "zone.4", 
                         "zone.3", 
                         "zone.2")
drone.eff <- contrast(drone.marginal,
                      alpha = 0.05,
                      method = "eff",
                      adjust = "tukey")
drone.pairwise <- contrast(drone.marginal,
                           alpha = 0.05,
                           method = "pairwise",
                           adjust = "tukey")
summary(drones.lmm)
anova(drones.lmm)
drone.cld
drone.eff
drone.pairwise
```
##### Plots
```{r}
drone.cld$.group=gsub(" ", "", drone.cld$.group)
ggplot(data = drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "black") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 1.5),
             color = "black") + 
  scale_y_continuous(limits = c(0, 25),
                     expand = c(0, 0)) +
  ylab("Least square mean drone production") + 
  xlab("Treatment") +
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment")
```

### 2-way ANOVA: days to first drone
##### Gather data
```{r}
mc.all.t2drone.df <- bind_rows(
  select(mc1.df, 
         id, 
         treatment, 
         date, 
         n_new_drones, 
         fd_day),
  select(mc2.df,
         id,
         treatment,
         date,
         n_new_drones,
         fd_day), 
  select(mc3.df,
         id,
         treatment,
         date,
         n_new_drones,
         fd_day),
  .id = "rep")

mc.all.t2drone.df <- mc.all.t2drone.df %>%
  group_by(id, rep, treatment) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  mutate(start_date = first(date)) %>%
  group_by(id, rep, treatment, start_date) %>%
  summarise(index_to_drone = min(which(csum_drones > 0)),
            date_to_drone = date[index_to_drone]) %>%
  mutate(days_to_drone = (as.duration(ymd(start_date) %--% date_to_drone / 86400))) %>%
  filter(!is.na(days_to_drone))
mc.all.t2drone.df <- mc.all.t2drone.df %>%
  mutate(trt_pulse = ifelse(id >= 3, 
                            "pulse",
                            "constant"),
         trt_total = ifelse(id < 2 | id > 4,
                            "60",
                            "100"))
```

##### Model specification
```{r}
t2drone.lmm <- lme(days_to_drone ~ trt_total * trt_pulse * rep,
                   random = ~ 1 | id,
                   data = mc.all.t2drone.df, 
                   na.action = na.exclude)
t2drone.marginal <- lsmeans(t2drone.lmm, ~ trt_pulse * trt_total)
t2drone.cld <- cld(t2drone.marginal,
                   alpha = 0.05,
                   Letters = letters,
                   adjust = "tukey")
t2drone.cld$treatment <- c("zone.4", 
                           "zone.2", 
                           "zone.3", 
                           "zone.1")
t2drone.eff <- contrast(t2drone.marginal,
                        alpha = 0.05,
                        method = "eff",
                        adjust = "tukey")
t2drone.pairwise <- contrast(t2drone.marginal,
                             alpha = 0.05,
                             method = "pairwise",
                             adjust = "tukey")
summary(t2drone.lmm)
anova(t2drone.lmm)
t2drone.cld
t2drone.eff
t2drone.pairwise
```
##### Plots
```{r}
t2drone.cld$.group=gsub(" ", "", t2drone.cld$.group)
ggplot(data = t2drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 2),
             color = "black") + 
  scale_y_continuous(limits = c(0, 35),
                     expand = c(0, 0)) +
  ylab("Least square mean days to first drone") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

### 2-way ANOVA: drone mass
##### Model specification
```{r}
dronemass.lmm <- lm(avg.individ.mass ~ trt_total * trt_pulse * rep,
                     data = mc.dronemass.all.df,
                     na.action = na.exclude)
dronemass.marginal <- lsmeans(dronemass.lmm, ~ trt_pulse * trt_total)
dronemass.cld <- cld(dronemass.marginal,
                     alpha = 0.05,
                     Letters = letters,
                     adjust = "tukey")
dronemass.cld$treatment <- c("zone.1", 
                             "zone.4", 
                             "zone.2", 
                             "zone.3")
dronemass.eff <- contrast(dronemass.marginal,
                          alpha = 0.05,
                          method = "eff",
                          adjust = "tukey")
dronemass.pairwise <- contrast(dronemass.marginal,
                               alpha = 0.05,
                               method = "pairwise",
                               adjust = "tukey")
summary(t2drone.lmm)
anova(t2drone.lmm)
dronemass.cld
dronemass.eff
dronemass.pairwise
```

##### Plots
```{r}
dronemass.cld$.group=gsub(" ", "", dronemass.cld$.group)
ggplot(data = dronemass.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 0.01),
             color = "black") + 
  scale_y_continuous(limits = c(0, .2),
                     expand = c(0, 0)) +
  ylab("LS mean mass per drone") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

### 2-way ANOVA: drone IT distance
##### Model specification

##### Plots

## FOOD CONSUMPTION
### 2-way ANOVA: total pollen consumption
##### Gather data
```{r}
mc.all.npcons.df <- mc.feed.all.df %>%
  ungroup() %>%
  group_by(id, treatment, rep) %>%
  summarise(total_p_cons = sum(p_mass_cons_avg, 
                               na.rm = TRUE),
            total_n_cons = sum(n_mass_cons, 
                               na.rm = TRUE)) %>%
  mutate(trt_pulse = ifelse(id >= 3, 
                            "pulse",
                            "constant"),
         trt_total = ifelse(id < 2 | id > 4,
                            "60",
                            "100"))
```

##### Model specification
```{r}
pcons.lmm <- lme(total_p_cons ~ trt_pulse * trt_total * rep,
                 random = ~ 1 | id,
                 data = mc.all.npcons.df,
                 na.action = na.exclude)
pcons.marginal <- lsmeans(pcons.lmm, ~ trt_pulse * trt_total)
pcons.cld <- cld(pcons.marginal,
                 alpha = 0.05,
                 Letters = letters,
                 adjust = "tukey")
pcons.cld$treatment <- c("zone.1", 
                         "zone.4", 
                         "zone.3", 
                         "zone.2")
pcons.eff <- contrast(pcons.marginal,
                      alpha = 0.05,
                      method = "eff",
                      adjust = "tukey")
pcons.pairwise <- contrast(pcons.marginal,
                           alpha = 0.05,
                           method = "pairwise",
                           adjust = "tukey")
summary(pcons.lmm)
anova(pcons.lmm)
pcons.cld
pcons.eff
pcons.pairwise
```

##### Plots
```{r}
pcons.cld$.group <- gsub(" ", "", pcons.cld$.group)
ggplot(data = pcons.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "black") + 
  scale_y_continuous(limits = c(0, 20),
                     expand = c(0, 0)) +
  ylab("Least square mean total pollen consumption (grams)") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```
### RM ANOVA: pollen consumption
##### Gather data
```{r}
mc.feed.all.df$p_mass_cons[is.na(mc.feed.all.df$p_mass_cons)] <- 0
mc.feed.all.df$n_mass_cons[is.na(mc.feed.all.df$n_mass_cons)] <- 0
mc.feed.all.cum.df <- mc.feed.all.df %>%
  ungroup() %>%
  group_by(id, rep) %>%
  mutate(total_p_cons = cumsum(p_mass_cons_avg),
         total_n_cons = cumsum(n_mass_cons)) %>%
  filter(fd_day != 0) %>%
  mutate(trt_pulse = ifelse(id >= 3, 
                            "pulse",
                            "constant"),
         trt_total = ifelse(id < 2 | id > 4,
                            "60",
                            "100"))
```

##### Model specification
```{r}
pcons.rmlmm = lme(total_p_cons ~ trt_total * trt_pulse * rep + date,
                  random = ~ 1 | id,
                  data = mc.feed.all.cum.df,
                  na.action = na.exclude)
pcons.acf <- ACF(pcons.rmlmm)
pcons.acf <- pcons.acf %>%
  filter(lag == 1) %>%
  select(ACF)
pcons.rmlmm.1 = lme(total_p_cons ~ trt_total * trt_pulse * rep + date, 
                    random = ~ 1 | id,
                    data = mc.feed.all.cum.df,
                    correlation = corAR1(form = ~ date | id,
                                         value = pcons.acf),
                    na.action = na.exclude,
                    method = "REML")
pcons.gwm.df <- groupwiseMean(total_p_cons ~ treatment + fd_day,
                              data = mc.feed.all.cum.df,
                              conf = 0.95,
                              digits = 3)
summary(pcons.rmlmm.1)
anova(pcons.rmlmm.1)
```

##### Plots
```{r}
pcons.gwm.df %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = Mean,
                       group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean cumulative pollen consumption") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(pcons.gwm.df$fd_day))
```

### 2-way ANOVA: total nectar consumption
##### Model specification
```{r}
ncons.lmm <- lme(total_n_cons ~ trt_pulse * trt_total * rep,
                 random = ~ 1 | id,
                 data = mc.all.npcons.df,
                 na.action = na.exclude)
ncons.marginal <- lsmeans(ncons.lmm, ~ trt_pulse * trt_total)
ncons.cld <- cld(ncons.marginal,
                 alpha = 0.05,
                 Letters = letters,
                 adjust = "tukey")
ncons.cld$treatment <- c("zone.4", 
                         "zone.1", 
                         "zone.3", 
                         "zone.2")
ncons.eff <- contrast(ncons.marginal,
                      alpha = 0.05,
                      method = "eff",
                      adjust = "tukey")
ncons.pairwise <- contrast(ncons.marginal,
                           alpha = 0.05,
                           method = "pairwise",
                           adjust = "tukey")
summary(ncons.lmm)
anova(ncons.lmm)
ncons.cld
ncons.eff
ncons.pairwise
```

##### Plots
```{r}
ncons.cld$.group=gsub(" ", "", ncons.cld$.group)
ggplot(data = ncons.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 5),
            color = "black") + 
  scale_y_continuous(limits = c(0, 150),
                     expand = c(0, 0)) +
  ylab("Least square mean total nectar consumption (grams)") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

### RM ANOVA: nectar consumption
##### Model specification
```{r}
ncons.rmlmm = lme(total_n_cons ~ trt_total * trt_pulse * rep + date,
                  random = ~ 1 | id,
                  data = mc.feed.all.cum.df,
                  na.action = na.exclude)
ncons.acf <- ACF(ncons.rmlmm)
ncons.acf <- ncons.acf %>%
  filter(lag == 1) %>%
  select(ACF)
ncons.rmlmm.1 = lme(total_n_cons ~ trt_total * trt_pulse * rep + date, 
                    random = ~ 1 | id,
                    data = mc.feed.all.cum.df,
                    correlation = corAR1(form = ~ date | id,
                                         value = ncons.acf),
                    na.action = na.exclude,
                    method = "REML")
ncons.gwm.df <- groupwiseMean(total_n_cons ~ treatment + fd_day,
                              data = mc.feed.all.cum.df,
                              conf = 0.95,
                              digits = 3)
summary(ncons.rmlmm.1)
anova(ncons.rmlmm.1)
```

##### Plots
```{r}
ncons.gwm.df %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = Mean,
                       group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean cumulative nectar consumption") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(ncons.gwm.df$fd_day))
```

## MISCELLANEOUS
## 2-way ANOVA: worker mortality 
##### Gather data
```{r}
mc.all.work.df <- bind_rows(
  select(mc1.df, 
         id, 
         treatment, 
         date, 
         n_worker_deaths, 
         fd_day),
  select(mc2.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day), 
  select(mc3.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day),
  .id = "rep")
mc.all.work.df <- mc.all.work.df %>%
  group_by(id, rep, treatment) %>%
  summarise(total_worker_deaths = sum(n_worker_deaths)) %>%
  mutate(trt_pulse = ifelse(id >= 3, 
                            "pulse",
                            "constant"),
         trt_total = ifelse(id < 2 | id > 4,
                            "60",
                            "100"))
```

##### Model specification
```{r}
workmort.lmm <- lme(total_worker_deaths ~ trt_pulse * trt_total * rep,
                    random = ~ 1 | id,
                    data = mc.all.work.df,
                    na.action = na.exclude)
workmort.marginal <- lsmeans(workmort.lmm, ~ trt_pulse * trt_total)
workmort.cld <- cld(workmort.marginal,
                    alpha = 0.05,
                    Letters = letters,
                    adjust = "tukey")
workmort.cld$treatment <- c("zone.2", 
                            "zone.1", 
                            "zone.3", 
                            "zone.4")
workmort.eff <- contrast(workmort.marginal,
                         alpha = 0.05,
                         method = "eff",
                         adjust = "tukey")
workmort.pairwise <- contrast(workmort.marginal,
                              alpha = 0.05,
                              method = "pairwise",
                              adjust = "tukey")
summary(workmort.lmm)
anova(workmort.lmm)
workmort.cld
workmort.eff
workmort.pairwise
```

##### Plots
```{r}
workmort.cld$.group=gsub(" ", "", workmort.cld$.group)
ggplot(data = workmort.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "black") + 
  scale_y_continuous(limits = c(0, 20),
                     expand = c(0, 0)) +
  ylab("Least square mean worker mortality") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

## Pollen per male
### 2-way ANOVA: worker mortality 
##### Gather data
```{r}
mc.feed.total.df <- mc.feed.all.df %>%
  ungroup() %>%
  group_by(id, rep, treatment) %>%
  summarise(
    total_p_cons = sum(p_mass_cons,
                       na.rm = TRUE),
    total_n_cons = sum(n_mass_cons,
                       na.rm = TRUE),
    total_p_fd = sum(p_mass_fd,
                     na.rm = TRUE),
    total_n_fd = sum(p_mass_fd,
                     na.rm = TRUE)
  )
mc.feed2drone.df <- mc.feed.total.df %>%
  left_join(select(mc.drone.all.df,
                   id, total_drones, rep),
            by = c("id" = "id", "rep" = "rep")) %>%
  mutate(p_per_drone = total_p_cons / total_drones,
         n_per_drone = total_n_cons / total_drones) %>%
  filter(p_per_drone != Inf)
mc.feed2drone.df <- mc.feed2drone.df %>%
  mutate(trt_pulse = ifelse(id >= 3, 
                            "pulse",
                            "constant"),
         trt_total = ifelse(id < 2 | id > 4,
                            "60",
                            "100"))
```
##### Model specification
```{r}
pdrone.lmm <- lme(p_per_drone ~ trt_pulse * trt_total * rep,
                  random = ~ 1 | id,
                  data = mc.feed2drone.df,
                  na.action = na.exclude)
pdrone.marginal <- lsmeans(pdrone.lmm, ~ trt_pulse * trt_total)
pdrone.cld <- cld(pdrone.marginal,
                  alpha = 0.05,
                  Letters = letters,
                  adjust = "tukey")
pdrone.cld$treatment <- c("zone.2", 
                          "zone.4", 
                          "zone.3", 
                          "zone.1")
pdrone.eff <- contrast(pdrone.marginal,
                       alpha = 0.05,
                       method = "eff",
                       adjust = "tukey")
pdrone.pairwise <- contrast(pdrone.marginal,
                            alpha = 0.05,
                            method = "pairwise",
                            adjust = "tukey")
summary(pdrone.lmm)
anova(pdrone.lmm)
pdrone.cld
pdrone.eff
pdrone.pairwise
```

##### Plots
```{r}
pdrone.cld$.group=gsub(" ", "", pdrone.cld$.group)
ggplot(data = pdrone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 0.1),
             color = "black") + 
  scale_y_continuous(limits = c(0, 1.25),
                     expand = c(0, 0)) +
  ylab("LSM pollen to produce drone (grams)") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

## Nectar per male
### 2-way ANOVA: worker mortality 
##### Model specification
```{r}
ndrone.lmm <- lme(n_per_drone ~ trt_pulse * trt_total * rep,
                  random = ~ 1 | id,
                  data = mc.feed2drone.df,
                  na.action = na.exclude)
ndrone.marginal <- lsmeans(ndrone.lmm, ~ trt_pulse * trt_total)
ndrone.cld <- cld(ndrone.marginal,
                  alpha = 0.05,
                  Letters = letters,
                  adjust = "tukey")
ndrone.cld$treatment <- c("zone.2", 
                          "zone.4", 
                          "zone.3", 
                          "zone.1")
ndrone.eff <- contrast(ndrone.marginal,
                       alpha = 0.05,
                       method = "eff",
                       adjust = "tukey")
ndrone.pairwise <- contrast(ndrone.marginal,
                            alpha = 0.05,
                            method = "pairwise",
                            adjust = "tukey")
summary(pdrone.lmm)
anova(pdrone.lmm)
ndrone.cld
ndrone.eff
ndrone.pairwise
```

##### Plots
```{r}
ndrone.cld$.group=gsub(" ", "", ndrone.cld$.group)
ggplot(data = ndrone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "black") + 
  scale_y_continuous(limits = c(0, 25),
                     expand = c(0, 0)) +
  ylab("LSM nectar to produce drone (grams)") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

# Model tables 