---
title: "2018 Resource Pulse Microcolony Analysis - Round 3"
subtitle: "Data cleanup and summarization"
date: "2/1/2018"
output: html_notebook
---

### Import packages 
```{r}
library(tidyverse)
library(lubridate)
```

### Import data
```{r}
mc3.df <- read_csv("D2018_MicroCol_Round3.csv",
                   skip = 1,
                   col_names = c(
                     "id",
                     "date",
                     "time",
                     "initials",
                     "temp",
                     "humidity",
                     "activity",
                     "mc_mass",
                     "n_drones",
                     "n_new_drones",
                     "n_worker_deaths",
                     "brood",
                     "workers_replaced",
                     "drones_removed",
                     "drones_frz",
                     "p_mass_rm",
                     "n_mass_rm",
                     "p_mass_fd",
                     "n_mass_fd",
                     "notes"),
                     na = c(" ", "N/A", "x")
                   )
mc3.df$date <- mdy(mc3.df$date)

mc3.end.df <- read_csv("./D2018_MicroCol_Round3_BroodMass.csv",
                       skip = 1,
                       col_names = c("id",
                                     "end_mass_comb",
                                     "notes"))
mc3.df$treatment <- ifelse(
  mc3.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc3.df$id < 3 & mc3.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc3.df$id < 4 & mc3.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc3.end.df$treatment <- ifelse(
  mc3.end.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc3.end.df$id < 3 & mc3.end.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc3.end.df$id < 4 & mc3.end.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc3.df <- mc3.df %>%
  group_by(id) %>%
  mutate(fd_day = row_number())
```

### Calculate food consumption/colony growth
#### Pull relevant vars
```{r}
mc3.feed.df <- tibble(id= mc3.df$id, 
                      date = mc3.df$date,
                      mc_mass = mc3.df$mc_mass,
                      p_mass_rm = mc3.df$p_mass_rm,
                      p_mass_fd = mc3.df$p_mass_fd,
                      n_mass_fd = mc3.df$n_mass_fd,
                      n_mass_rm = mc3.df$n_mass_rm,
                      treatment = mc3.df$treatment,
                      fd_day = mc3.df$fd_day)
```

#### Colony initiation mass + pollen added
```{r}
mc3.feed.init <- mc3.feed.df[mc3.feed.df$fd_day == 1, ]
mc3.feed.init$n_mass_rm <- NA
mc3.feed.init$n_mass_fd <- NA
mc3.feed.init$p_mass_fd <- 3.000
mc3.feed.init$fd_day <- 0

mc3.feed.df <- mc3.feed.df %>%
  bind_rows(mc3.feed.init) %>%
  arrange(id, fd_day) %>%
  filter(id != 2.7)
mc3.df$id <- as.factor(mc3.df$id)
```

#### Pollen start and stop points, etc.
```{r}
pollen.subtract.r3 <- mc3.feed.df %>%
  filter(!is.na(p_mass_rm))
pollen.subtract.r3 <- as.vector(pollen.subtract.r3$p_mass_rm)

mc3.feed.df$p_mass_rm[mc3.feed.df$p_mass_fd == 3] <- 0.0 

start.r3 <- which(!is.na(mc3.feed.df$p_mass_rm))
stop.r3 <- start.r3 - 1 # stop points are 1 behind the start
#start.r2 <- head(start.r2, -1) # trim off last start index
stop.r3 <- tail(stop.r3, -1) # trim off first stop index to correctly align
stop.r3 <- c(stop.r3, 486)

print(start.r3)
print(stop.r3)
```

#### Calculate total pollen provided/consumed
```{r}
pollen.sum.r3 <- c(rep(0, length(start.r3)))
for (i in 1:length(start.r3)) {
  for (j in start.r3[i]:stop.r3[i]) {
    pollen.sum.r3[i] <- pollen.sum.r3[i] + mc3.feed.df$p_mass_fd[j]
  }
}
print(pollen.sum.r3)
length(pollen.subtract.r3)
length(pollen.sum.r3)

length(pollen.subtract.r3) == length(pollen.sum.r3 - pollen.subtract.r3) #FALSE

psum.rm.r3 <- seq(6, 162, by = 6) # Index pos. of each 
pollen.sum.r3 <- pollen.sum.r3[-psum.rm.r3]
print(pollen.sum.r3)
length(pollen.subtract.r3) == length(pollen.sum.r3)
```

```{r}
pollen.consumed.r3 <- pollen.sum.r3 - pollen.subtract.r3
print(pollen.consumed.r3)
```

##### Add pollen consumed column
```{r}
mc3.feed.df$p_mass_cons <- NA
pcons.index.r3 <- stop.r3[-psum.rm.r3]
mc3.feed.df$p_mass_cons[pcons.index.r3 + 1] <- pollen.consumed.r3
mc3.feed.df$p_mass_cons[which(mc3.feed.df$p_mass_rm == 0)] <- 0.00
```

#### Calculate average daily pollen/nectar consumption
```{r}
mc3.feed.df$p_mass_cons_avg <- NA
fd_days.r3 <- ((stop.r3 - start.r3) + 1)
mc3.feed.df$p_mass_cons_avg[which(!is.na(mc3.feed.df$p_mass_cons))] <-
  mc3.feed.df$p_mass_cons[which(!is.na(mc3.feed.df$p_mass_cons))] / fd_days.r3
mc3.feed.df <- fill(mc3.feed.df, 
                    p_mass_cons_avg, 
                    .direction = "up")
mc3.feed.df$p_mass_cons_avg[mc3.feed.df$p_mass_cons_avg == 0] <- NA
mc3.feed.df$p_mass_cons_avg <- as.numeric(mc3.feed.df$p_mass_cons_avg) # for some 
# reason it was boolean...? 
mc3.feed.df$n_mass_cons <- NA
mc3.feed.df$n_mass_rm <- as.numeric(mc3.feed.df$n_mass_rm)
mc3.feed.df$n_mass_cons <- mc3.feed.df$n_mass_fd - lead(mc3.feed.df$n_mass_rm)
mc3.feed.df$n_mass_cons <- as.numeric(mc3.feed.df$n_mass_cons)
mc3.feed.df$treatment <- as.factor(mc3.feed.df$treatment)
```

### Calculate true mass 
```{r}
mc3.feed.df <- mc3.feed.df %>%
  group_by(id) %>%
  mutate(fd_day_count = c(0, rep(seq(3, 1, by = -1), 5), 0, 0))

mc3.feed.df <- mc3.feed.df %>%
  group_by(id) %>%
  mutate(mc_mass_init = mc_mass[fd_day == 0] - 3)
mc3.feed.df <- mc3.feed.df %>%
  ungroup() %>%
  mutate(mc_mass_true = ifelse(
    fd_day_count == 3,
    ((mc_mass - mc_mass_init) + p_mass_cons_avg),
    ifelse(
      fd_day_count == 2,
      (((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) + p_mass_cons_avg),
      ifelse(
        fd_day_count == 1,
        ((((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) - lag(p_mass_fd, n = 2)) + p_mass_cons_avg),
        0
        )
      )
    ))
mc3.feed.df$mc_mass_true[mc3.feed.df$mc_mass_true == 0] <- NA
mc3.feed.df$mc_mass_true[mc3.feed.df$fd_day == 0] <- 0.00
mc3.feed.df$date[mc3.feed.df$mc_mass_true == 0] <- "2018-11-10"
mc3.feed.df[82, 3] <- 425.91 # Fix mis-recording in data frame
mc3.feed.df[473, 5] <- 1.59# Fix mis-recording in data frame
```

#### Calculate avg. mass difference
```{r}
mc3.feed.df <- mc3.feed.df %>%
  mutate(mc_mass_diff = c(NA, diff(mc_mass_true)))
```

### Create time category relative to pulse
```{r}
mc3.feed.df <- mc3.feed.df %>%
  ungroup() %>%
  mutate(pulse_cat = ifelse(
    fd_day <= 3, 
    "b1",
    ifelse(
      fd_day > 3 & fd_day <= 6,
      "p1",
      ifelse(
        fd_day > 6 & fd_day <= 10,
        "a1.b2",
        ifelse(fd_day >10 & fd_day <= 13,
               "p2",
               "a2")
      )
    )
  ))
mc3.feed.df$pulse_cat <- as.factor(mc3.feed.df$pulse_cat)
```
### Drone cleanup 
```{r}
mc3.drone.df <- mc3.df %>%
  ungroup() %>%
  group_by(id, treatment) %>%
  summarise(total_drones = sum(n_new_drones, na.rm = TRUE))
mc3.drone.mass.df <- read_csv("./D2018_mc3_dronemass.csv", 
                              skip = 1,
                              col_names = c("date",
                                            "id",
                                            "n_drones",
                                            "total_mass",
                                            "avg_drone_mass"))
mc3.drone.mass.df$date <- mdy(mc3.drone.mass.df$date)
mc3.drone.mass.df$treatment <- ifelse(
  mc3.drone.mass.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc3.drone.mass.df$id < 3 & mc3.drone.mass.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc3.drone.mass.df$id < 4 & mc3.drone.mass.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)s
```

### Save all data to working directory
#### All Round 3
```{r}
write_csv(mc3.df, "D2018_microcol_round3_clean.csv")
write_csv(mc3.feed.df, "D2018_microcol_round3_feed_clean.csv")
write_csv(mc3.drone.df, "D2018_microcol_round3_drone.csv")
```

