---
title: "2018 Resource Pulse Microcolony Analysis - Round 1"
subtitle: "Data cleanup and summarization"
date: "2/1/2018"
output: html_notebook
---

### Import packages
```{r}
library(tidyverse)
library(lubridate)
library(zoo)
```

### Import data
```{r}
mc1.df <- read_csv("D2018_MicroCol_Round1.csv", skip = 2, 
                   col_names = c(
                     "id",
                     "date",
                     "time",
                     "initials",
                     "n_new_drones",
                     "n_drones",
                     "n_worker_deaths",
                     "age_class",
                     "workers_replaced",
                     "drones_removed",
                     "activity",
                     "dom_worker",
                     "mc_mass",
                     "p_mass_rm",
                     "n_mass_rm",
                     "p_mass_fd",
                     "n_mass_fd",
                     "n_culled",
                     "frozen?",
                     "temp",
                     "humidity"
                   ), 
                   na = c("-", "", " "))
# Change date column to an actual date format
mc1.df$date <- paste(mc1.df$date, "2018", sep = "/")
mc1.df$date <- mdy(mc1.df$date)

# Remove end values from data frame that aren't used in plotting/analysis
# 1.5 was repeated in data entry 
mc1.df <- mc1.df[-c(409:425), ]

# Remove unused columns from data frame
mc1.df$initials = NULL
mc1.df$time = NULL
mc1.df$n_culled = NULL
mc1.df$dom_worker = NULL
mc1.df$`frozen?` = NULL
mc1.df$age_class = NULL

# Bind final observations not on MC data sheets
mc1.end.df <- read_csv("D2018_MicroCol_Breakdown.csv", skip = 1,
                       col_names = c("id", 
                                     "end_mc_mass", 
                                     "end_mass_comb", 
                                     "mass_box", 
                                     "date"))
mc1.df$id <- as.numeric(mc1.df$id)
mc1.df$treatment <- ifelse(mc1.df$id < 2,
                           paste("zone.1"),
                           ifelse(
                             mc1.df$id < 3 & mc1.df$id > 1,
                             paste("zone.2"),
                             ifelse(mc1.df$id < 4 & mc1.df$id > 3, 
                                    paste("zone.3"), 
                                    paste("zone.4"))
                           ))
mc1.end.df$treatment <- ifelse(mc1.end.df$id < 2,
                           paste("zone.1"),
                           ifelse(
                             mc1.end.df$id < 3 & mc1.end.df$id > 1,
                             paste("zone.2"),
                             ifelse(mc1.end.df$id < 4 & mc1.end.df$id > 3, 
                                    paste("zone.3"), 
                                    paste("zone.4"))
                           ))
mc1.df <- mc1.df %>%
dplyr::group_by(id) %>%
dplyr::mutate(fd_day = row_number())
mc1.df$id <- as.factor(mc1.df$id)
```

### Calculate food consumption/colony growth
#### Pull relevant vars
```{r}
mc1.feed.df <- data_frame(id = mc1.df$id, 
                   date = mc1.df$date,
                   mc_mass = mc1.df$mc_mass,
                   p_mass_rm = mc1.df$p_mass_rm, 
                   p_mass_fd = mc1.df$p_mass_fd, 
                   n_mass_fd = mc1.df$n_mass_fd, 
                   n_mass_rm = mc1.df$n_mass_rm,
                   treatment = mc1.df$treatment,
                   fd_day = mc1.df$fd_day)
```

#### Colony initiation mass + pollen added
```{r}
mc1.feed.init <- mc1.feed.df[mc1.feed.df$fd_day == 1, ]
mc1.feed.init$n_mass_rm <- NA
mc1.feed.init$n_mass_fd <- NA
mc1.feed.init$p_mass_fd <- 2.000
mc1.feed.init$fd_day <- 0

mc1.feed.df$p_mass_rm[is.na(mc1.feed.df$p_mass_fd)] <- 0.00 # Add 0 for start position on replicate
mc1.feed.df$p_mass_fd[is.na(mc1.feed.df$p_mass_fd)] <- 2.00 # Initial feed for all treatments
# mc1.feed.df <- mc1.feed.df %>%
#   bind_rows(mc1.feed.init) %>%
#   arrange(id, fd_day) %>%
#   filter(id != 2.4)
```

#### Pollen start and stop points, etc.
```{r}
pollen.subtract.r1 <- mc1.feed.df %>%
  filter(!is.na(p_mass_rm))
pollen.subtract.r1 <- as.vector(pollen.subtract.r1$p_mass_rm)
pollen.subtract.r1 <- tail(pollen.subtract.r1, -1)
start.r1 <- which(!is.na(mc1.feed.df$p_mass_rm))
stop.r1 <- start.r1 - 1 # stop points are 1 behind the start
start.r1 <- head(start.r1, -1) # trim off last start index
stop.r1 <- tail(stop.r1, -1) # trim off first stop index to correctly align

print(start.r1)
print(stop.r1)

```

#### Calculate total pollen provided/consumed
```{r}
pollen.sum.r1 <- c(rep(0, length(start.r1))) # Initialize pollen.sum vector
for (i in 1:length(start.r1)) {
    for (j in start.r1[i]:stop.r1[i]) {
      pollen.sum.r1[i] <- pollen.sum.r1[i] + mc1.feed.df$p_mass_fd[j]
  }
}
pollen.subtract.r1[pollen.subtract.r1 == 0] <- NA # Replace 0's (start points) with NA
pollen.consumed.r1 <- pollen.sum.r1 - pollen.subtract.r1 # Calculate differences - NA's 
# for very last feed as we didn't measure final pollen remaining
length(pollen.subtract.r1) == length(pollen.sum.r1 - pollen.subtract.r1) # Check to see that
```

##### Add pollen consumed column
```{r}
mc1.feed.df$p_mass_cons <- NA # Create column for pollen consumption
mc1.feed.df$p_mass_cons[stop.r1 + 1] <- pollen.consumed.r1
```

#### Calculate average daily pollen/nectar consumption
```{r}
mc1.feed.df$p_mass_cons_avg <- NA 
fd.days.r1 <- ((stop.r1 - start.r1) + 1)
mc1.feed.df$p_mass_cons_avg[which(!is.na(mc1.feed.df$p_mass_cons)) - 1] <-
  mc1.feed.df$p_mass_cons[which(!is.na(mc1.feed.df$p_mass_cons))] / fd.days.r1
mc1.feed.df$p_mass_cons_avg[mc1.feed.df$fd_day == 17] <- 0
mc1.feed.df <- fill(mc1.feed.df, 
                    p_mass_cons_avg, 
                    .direction = "up")
mc1.feed.df$p_mass_cons_avg[mc1.feed.df$p_mass_cons_avg == 0] <- NA
mc1.feed.df$n_mass_cons <- NA
mc1.feed.df$n_mass_rm[which(is.na(mc1.feed.df$n_mass_rm))] <- 0.00 
mc1.feed.df$n_mass_cons <- mc1.feed.df$n_mass_fd - lead(mc1.feed.df$n_mass_rm)
mc1.feed.df <- mc1.feed.df %>%
  mutate(n_mass_cons = lag(n_mass_cons, 1))
mc1.feed.df$n_mass_cons[which(mc1.feed.df$n_mass_rm == 0)] <- NA
mc1.feed.df$n_mass_cons[which(is.na(mc1.feed.df$n_mass_cons))] <- 0.00
```

### Calculate true mass 
```{r}
# Old way to do fd.days.count
x <- list()
y <- 0
for (i in fd.days.r1) {
  y <- y + 1
  if (i == 4) {
    z <- 3:0
  } else {
    z <- 3:1
  }
  x[[y]] <- z
}
fd_days_count.r1 <- unlist(x)
fd_days_count.r1 <- c(fd_days_count.r1, c(NA, NA, NA))
mc1.feed.df$fd_day_count <- fd_days_count.r1
# mc1.feed.df <- mc1.feed.df %>%
#   ungroup() %>%
#   group_by(id) %>%
#   mutate(fd.day.count = c(1, 2, 3, 0, 1, 2, 3, 0, 1, 2, 3, 0, 1, 2, 3, 1 ,2))
mc1.feed.df <- mc1.feed.df %>%
  group_by(id) %>%
  mutate(mc_mass_init = mc_mass[fd_day == 1] - 2)
mc1.feed.df <- mc1.feed.df %>%
  ungroup() %>%
  mutate(mc_mass_true = ifelse(
    fd_day_count == 1,
    ((mc_mass - mc_mass_init) + p_mass_cons_avg),
    ifelse(
      fd_day_count == 2,
      (((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) + p_mass_cons_avg),
      ifelse(
        fd_day_count == 3,
        ((((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) - lag(p_mass_fd, n = 2)) + p_mass_cons_avg),
        ifelse(fd_day_count == 0,
               ((((mc_mass - mc_mass_init) - lag(p_mass_fd, n = 1)) - lag(p_mass_fd, n = 2)) - lag(p_mass_fd, n = 3)) + p_mass_cons_avg, 0)
      )
    )
  ))

mc1.feed.df <- mc1.feed.df %>%
  ungroup() %>%
  arrange(id, fd_day)
mc1.end.df <- mc1.end.df %>%
  ungroup() %>%
  arrange(id)
mc1.feed.df$mc_mass_true[mc1.feed.df$fd_day == 17] <- mc1.end.df$end_mass_comb
```

#### Interpolate missing `mc_mass_true` values
```{r}
mc1.feed.df <- mc1.feed.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(mc_mass_true_intrp = na.approx(mc_mass_true, 
                                        maxgap = 4,
                                        rule = 2))
```

#### Remove last 3 masses
These aren't accurate given that we didn't measure pollen consumption for when the exp. ended for this round.
```{r}
mc1.feed.df$mc_mass_true_intrp[is.na(mc1.feed.df$p_mass_cons_avg)] <- NA
```

#### Calculate avg. mass difference
```{r}
mc1.feed.df <- mc1.feed.df %>%
  mutate(mc_mass_diff = c(NA, diff(mc_mass_true_intrp)))
```

### Create time category relative to pulse
```{r}
mc1.feed.df <- mc1.feed.df %>%
  ungroup() %>%
  mutate(pulse_cat = ifelse(
    fd_day <= 4, 
    "b1",
    ifelse(
      fd_day > 4 & fd_day <= 7,
      "p1",
      ifelse(
        fd_day > 7 & fd_day <= 11,
        "a1.b2",
        ifelse(fd_day >11 & fd_day <= 14,
               "p2",
               "a2")
      )
    )
  ))
mc1.feed.df$pulse_cat <- as.factor(mc1.feed.df$pulse_cat)
```

### Clean drone data
```{r}
mc1.drone.df <- mc1.df %>%
  ungroup() %>%
  group_by(id, treatment) %>%
  summarise(total_drones = sum(n_new_drones, 
                               na.rm = TRUE))
```

#### Import data
```{r}
mc1.drone.it.df <- read_csv("./D2018_MC1_DroneIT.csv")
mc1.drone.mass.df <- read_csv("./D2018_MC1_DroneMass.csv",
                              skip = 1,
                              col_names = c("date",
                                            "id",
                                            "n_drones",
                                            "total_mass",
                                            "avg_drone_mass")) %>%
  mutate(avg_drone_mass = total_mass / n_drones)
mc1.drone.mass.df$date <- mdy(mc1.drone.mass.df$date)

```

#### Add vars, summarise
```{r}
mc1.drone.it.df$X5 <- NULL
mc1.drone.it.df$date <- mdy(mc1.drone.it.df$date)
mc1.drone.it.df <- mc1.drone.it.df %>%
  fill(date, 
       id, 
       .direction = "down")
mc1.drone.it.df$treatment <- ifelse(
  mc1.drone.it.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc1.drone.it.df$id < 3 & mc1.drone.it.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc1.drone.it.df$id < 4 & mc1.drone.it.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc1.drone.mass.df$treatment <- ifelse(
  mc1.drone.mass.df$id < 2,
  paste("zone.1"),
  ifelse(
    mc1.drone.mass.df$id < 3 & mc1.drone.mass.df$id > 1,
    paste("zone.2"),
    ifelse(
      mc1.drone.mass.df$id < 4 & mc1.drone.mass.df$id > 3,
      paste("zone.3"),
      paste("zone.4")
    )
  )
)
mc1.drone.it.df <- mc1.drone.it.df %>%
  filter(!is.na(it.distance))
mc1.drone.mass.df <- mc1.drone.mass.df %>%
  filter(!is.na(avg.individ.mass))
```

### Write cleaned data
```{r}
write_csv(mc1.df, "./D2018_microcol_round1_clean.csv") 
write_csv(mc1.feed.df, "./D2018_microcol_round1_feed_clean.csv")
write_csv(mc1.drone.df, "./D2018_microcol_round3_drone.csv")
write_csv(mc1.drone.it.df, "./D2018_microcol_round1_droneit_clean.csv")
write_csv(mc1.drone.mass.df, "./D2018_microcol_round1_dronemass_clean.csv")
```

