---
title: "2018 Resource Pulse Microcolony Analysis - Round 2"
subtitle: Analysis and model construction/selection
date: 12/18/2018
output: html_notebook
---

### Import packages 
```{r echo = TRUE, results = "hide"}
library(psych)
library(nlme) #lmer can't use temporal corrleation structures
library(car)
library(multcompView)
library(lsmeans)
library(tidyverse)
library(rcompanion)
library(lmtest)
library(gam)
library(gamm4)
library(mgcv)
```

### Load in data
```{r}
mc2.df <- read_csv("./D2018_MicroCol_Round1_Clean.csv")
mc2.feed.df <- read_csv("./D2018_MicroCol_Round1_Feed_Clean.csv")
mc2.drone.df <- read_csv("./D2018_MicroCol_Round2_Drones.csv")
mc2.drone.it.df <- read_csv()
mc2.drone.mass.df <- read_csv()
```

### RM ANOVA on mass gain
##### Temporal correlation structure
```{r}
mc2.mass.corr.model <- lme(mc_mass_true ~ treatment + date + treatment*date, 
                           random = ~ 1 | id,
                           data = mc2.feed.df,
                           na.action = na.exclude)

ACF(mc2.mass.corr.model) # Lag 1: 0.314
acf(mc2.feed.df$mc_mass_true, na.action = na.exclude)
```

##### Full model
```{r}
mc2.mass.model.1 = lme(mc_mass_true ~ treatment + date + treatment*date, 
                       random = ~ 1 | id,
                       data = mc2.feed.df,
                       correlation = corAR1(form = ~ date | id,
                                            value = 0.2833),
                       na.action = na.exclude,
                       method = "REML")
Anova(mc2.mass.model.1)
```

##### Fixed effects only w/comparison
```{r}
mc2.mass.model.1.fixed = gls(mc_mass_true ~ treatment + date + treatment*date,
                             data = mc2.feed.df,
                             method = "REML",
                             na.action = na.exclude)

anova(mc2.mass.model.1, mc2.mass.model.1.fixed)
```

##### Null model w/comparison
```{r}
mc2.mass.model.null <- lme(mc_mass_true ~ 1,
                           random = ~ 1 | id,
                           data = mc2.feed.df,
                           na.action = na.exclude)

nagelkerke(mc2.mass.model.1, 
           mc2.mass.model.null)
```

##### LS Means estimates
```{r}
mc2.mass.marginal <- lsmeans(mc2.mass.model.1, ~ treatment:date)

mc2.mass.cld <- cld(mc2.mass.marginal,
                    alpha   = 0.05, 
                    Letters = letters,
                    adjust  = "tukey")
mc2.mass.cld
```
```{r}
mc2.mass.cld$.group = gsub(" ", "", mc2.mass.cld$.group)
ggplot(data = mc2.mass.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  geom_text(mapping = aes(y = upper.CL + 0.5),
             color = "white") + 
  ylab("Least square mean estimated microcolony mass") + 
  xlab("Treatment")
```

##### Groupwise estimated means across exp
```{r}
mc2.feed.nona.df <- mc2.feed.df %>%
  filter(id != 1.4) %>%
  filter(!is.na(mc_mass_true))
mc2.mass.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  mc_mass_true ~ treatment + date,
  data = mc2.feed.nona.df,
  conf = 0.95,
  digits = 3
)

mc2.mass.gwm.df
```

Plot groupwise means from above
```{r}
pd = position_dodge(.2)
ggplot(data = mc2.mass.gwm.df, 
       mapping = aes(x = date,
                     y = Mean,
       color = treatment)) +
  geom_errorbar(aes(ymin = Trad.lower,
                    ymax = Trad.upper),
                  width = 0.2, 
                  size = 0.7, 
                  position = pd) +
  geom_point(size = 4, 
             position = pd) +
  theme_black() +
  theme(axis.title = element_text(face = "bold")) +
  ylab("Least square mean mass")
```

##### Model diagnostics
```{r}
mc2.model1.resid <- residuals(mc2.mass.model.1)
plotNormalHistogram(mc2.model1.resid)
plot(residuals(mc2.mass.model.1),
     fitted(mc2.mass.model.1))
plot(residuals(mc2.mass.model.1))
acf(residuals(mc2.mass.model.1), na.action = na.exclude)
```

### RM ANOVA on drone production (__may need GLMM due to count data__) 
##### Calculate cumulative drone production
```{r} 
mc2.cumdrone.df <- mc2.df %>%
  ungroup() %>%
  dplyr::filter(id != 1.4) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(fd.day = row_number()) %>%
  dplyr::mutate(csum_drones = cumsum(n_new_drones)) %>%
  dplyr::mutate(log_csum_drones = log(csum_drones + 1)) %>%
  dplyr::arrange(id, date)
mc2.cumdrone.df
```

##### Temporal correlation structure
```{r}
mc2.corr.model.cdrone = lme(log_csum_drones ~ treatment + date + treatment*date, 
                            random = ~ 1 | id,
                            data = mc2.cumdrone.df,
                            na.action = na.exclude)

ACF(mc2.corr.model.cdrone) # 1st order lag: 0.8272
acf(mc2.cumdrone.df$csum_drones)
```

##### Full model
```{r}
mc2.cdrone.model.1 = lme(log_csum_drones ~ treatment + date + treatment*date, 
                         random = ~ 1 | id,
                         data = mc2.cumdrone.df,
                         correlation = corAR1(form = ~ date | id,
                                              value = 0.747),
                         na.action = na.exclude,
                         method = "REML")
Anova(mc2.cdrone.model.1)
```

##### Fixed effects only w/comparison
```{r}
mc2.cdrone.model.1.fixed = gls(log_csum_drones ~ treatment + date + treatment*date,
                               data = mc2.cumdrone.df,
                               method = "REML",
                               na.action = na.exclude)

anova(mc2.cdrone.model.1, mc2.cdrone.model.1.fixed)
```

##### Null model w/comparison
```{r}
mc2.cdrone.model.null <- lme(log_csum_drones ~ 1,
                             random = ~ 1 | id,
                             data = mc2.cumdrone.df,
                             na.action = na.exclude)

nagelkerke(mc2.cdrone.model.1, 
           mc2.cdrone.model.null)
```

##### LS Means estimates
```{r}
mc2.cdrone.marginal <- lsmeans(mc2.cdrone.model.1,  ~ treatment:date)

mc2.drone.cld <- cld(mc2.cdrone.marginal,
                     alpha   = 0.05, 
                     Letters = letters,
                     adjust  = "tukey")
mc2.drone.cld
```

```{r}
mc2.drone.cld$.group = gsub(" ", "", mc2.drone.cld$.group)
ggplot(data = mc2.drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 0.15),
             color = "white") + 
  ylab("Least square mean drone production") + 
  xlab("Treatment")
```
##### Groupwise estimated means across exp
```{r}
mc2.drones.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  log_csum_drones ~ treatment + date,
  data = mc2.cumdrone.df,
  conf = 0.95,
  digits = 3
  )

mc2.drones.gwm.df
```

Plot groupwise means from above
```{r}
pd = position_dodge(.2)
ggplot(mc2.drones.gwm.df, aes(x = date,
                              y = Mean,
                              color = treatment)) +
  geom_errorbar(aes(ymin = Trad.lower,
                    ymax = Trad.upper),
                  width = 0.2, 
                  size = 0.7, 
                  position = pd) +
  geom_point(size = 4, 
               position = pd,
               alpha = 0.75) +
  theme_black() +
  theme(axis.title = element_text(face = "bold")) +
  ylab("Least-square mean cumulative drone production") + 
  xlab("Date of experiment")
```

##### Model diagnostics
```{r}
mc2.cdrone.model.1.resid <- residuals(mc2.cdrone.model.1)
plotNormalHistogram(mc2.cdrone.model.1.resid)
plot(residuals(mc2.cdrone.model.1),
     fitted(mc2.cdrone.model.1))
plot(mc2.cdrone.model.1)
plot(residuals(mc2.cdrone.model.1))
acf(residuals(mc2.cdrone.model.1))
```


### ANOVA for total drone production
##### Define & summarize model
```{r} 
mc2.drone.df <- mc2.drone.df %>%
  filter(id != 1.4)
mc2.drone.lm <- lm(total_drones ~ treatment,
                   data = mc2.drone.df)
tidy(mc2.drone.lm)
anova(mc2.drone.lm)
```

##### LS means calculation
```{r}
mc2.tdrone.marginal <- lsmeans(mc2.drone.lm,  ~ treatment)

mc2.tdrone.cld <- cld(mc2.tdrone.marginal,
                      alpha   = 0.05, 
                      Letters = letters,
                      adjust  = "tukey")
mc2.tdrone.cld
```

##### Plot LS means
```{r}
mc2.tdrone.cld$.group=gsub(" ", "", mc2.tdrone.cld$.group)
ggplot(data = mc2.tdrone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "white") + 
  theme_black() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 2),
             color = "white") + 
  ylab("Least square mean drone production") + 
  xlab("Treatment")
```

### GAM for drone production
##### Temporal correlation structure
```{r}
mc2.corr.model.cdrone = lme(csum_drones ~ treatment + date + treatment*date, 
                            random = ~ 1 | id,
                            data = mc2.cumdrone.df,
                            na.action = na.exclude)

ACF(mc2.corr.model.cdrone) # 1st order lag: 0.8272
acf(mc2.cumdrone.df$csum_drones)
```

##### Full model
```{r}
mc2.cumdrone.df$treatment <- as.factor(mc2.cumdrone.df$treatment)
mc2.model.1.cdrone.gam = gamm(csum_drones ~ treatment + date + treatment*date, 
                            random = list(id = ~ 1),
                            family = "poisson",
                            correlation = corAR1(form = ~ date | id),
                            data = mc2.cumdrone.df,
                            na.action = na.exclude)
summary(mc2.model.1.cdrone.gam$gam)
summary(mc2.model.1.cdrone.gam$lme)
```