---
title: "2018 Bumble Bee Microcolony Experiment"
output:
  html_document:
    df_print: paged
date: "11/29/2018"
subtitle: Summary figures
---
**Name:** Jeremy Hemberger
**Email:** j.hemberger.wisc@gmail.com

## Load packages
```{r}
library(tidyverse)
library(viridis)
library(lubridate)
```

## Round 1 Summary Plots 
#### Final comb mass

```{r}
mc1end.df %>%
  filter(!is.na(end_mass_comb)) %>%
  group_by(treatment) %>%
  summarise(mean.comb.mass = mean(end_mass_comb), 
            se = sd(end_mass_comb) / sqrt(n())) %>%
  ggplot() + 
  geom_col(mapping = aes(x = treatment, 
                         y = mean.comb.mass, 
                         fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(x = treatment, 
                                y = mean.comb.mass,
                                ymax = mean.comb.mass + se, 
                                ymin = mean.comb.mass - se),
                  color = "white") +
  scale_y_continuous(limits = c(0, 10)) + 
  theme_black()
```

#### Raw mass gain for all microcolony replicates
```{r}
ggplot(na.rm = TRUE) + 
  geom_line(data = mc1.df, mapping = aes(x = date, 
                                         y = true_mc_mass, 
                                         group = id, 
                                         color = treatment,
                                         na.rm = FALSE),
            size = 1.1) + 
  theme_black()
```

#### Total Males Produced as point range plot
```{r}
mc1.df %>%
  group_by(id, treatment) %>%
  filter(id != 2.4) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  group_by(treatment) %>%
  summarise(mean_males = mean(total_males), se = sd(total_males) / sqrt(n())) %>%
  ggplot() + 
  geom_pointrange(mapping = aes(x = treatment, y = mean_males, 
                                ymax = mean_males + se,
                                ymin = mean_males - se),
                  color = "white") + 
  theme_black()
```

#### Total males produced as boxplot
```{r}
mc1.df %>%
  group_by(id, treatment) %>%
  filter(id != 2.4) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  group_by(treatment) %>%
  ggplot(mapping = aes(x = treatment, y = total_males)) + 
  geom_boxplot(mapping = aes(fill = treatment),
               color = "white") + 
  theme_black()
```

#### Male production normalized across microcolonies - diverging dot plot
```{r}
mc1.df %>%
  group_by(id, treatment) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(drone_z = round((total_males - mean(total_males, na.rm = TRUE)) / sd(total_males, na.rm = TRUE), digits = 2)) %>%
  mutate(drone_score = ifelse(drone_z < 0, "below", "above")) %>%
  arrange(desc(drone_z)) %>%
  mutate(z_order = factor(`id`, 
                          levels = `id`)) %>%
  ggplot(aes(x = z_order, 
             y = drone_z, 
             label = drone_z)) + 
  geom_segment(mapping = aes(y = 0,
                             x = z_order,
                             yend = drone_z,
                             xend = z_order),
               size = 1.1,
               color = "white",
               alpha = 0.25) + 
  geom_point(stat = "identity", 
             mapping = aes(col = drone_score), 
             size = 8,
             alpha = 0.5) + 
  scale_color_manual(name = "Drone Production", 
                     labels = c("Above Average", "Below Average"),
                     values = c("above" = "green2", "below" = "red2")) + 
  geom_text(color = "white",
            size = 2) + 
  labs(y = "Drone Production Z-Score", 
       x = "Microcolony ID") + 
  coord_flip() + 
  theme_black() 
```

#### Drone production bump chart - by treatment
```{r}
mc1.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(fd.day = row_number()) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  arrange(id, date) %>%
  ggplot(mapping = aes(x = fd.day,
                       y = csum_drones,
                       group = id)) +
  geom_line(mapping = aes(color = treatment),
            alpha = 0.6,
            size = 1.5) +
  geom_point(mapping = aes(color = treatment),
             alpha = 0.75,
             size = 3) +
  annotate("rect",
           xmin = 4,
           xmax = 6,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
    annotate("rect",
           xmin = 11,
           xmax = 13,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  scale_x_continuous(breaks = unique(mc1.df$fd.day)) +
  labs(y = "Cumulative Drone Production",
       x = "Feeding Interval") + 
  theme_black()

```

#### Average mass gain - smoothed
```{r}
ggplot(data = mc1.df) + 
  # geom_point(mapping = aes(x = date, y = mc_mass, #- mass_box - lag(p_mass_fd),
  #                          color = treatment)) + 
  geom_smooth(span = 0.75, 
              mapping = aes(x = date, 
                            y = mc_mass, #- mass_box - lag(p_mass_fd), 
                            color = treatment,
                            fill = treatment)) + 
  theme_black()
```

#### Cumulative nectar consumptiion grouped by treatment
```{r}
mc1.feed.df %>%
  group_by(id) %>%
  mutate(cum_pollen = cumsum(p_mass_cons_avg), 
         cum_nectar = cumsum(n_mass_cons)) %>%
  group_by(date, treatment) %>%
  summarise(nectar_cons = mean(cum_nectar), 
            nectar_se = (sd(cum_nectar) / (sqrt(n()))), 
            pollen_cons = mean(cum_pollen, na.rm = TRUE), 
            pollen_se = (sd(cum_pollen, na.rm = TRUE) / (sqrt(n())))) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = date,
                      y = nectar_cons,
                      ymin = nectar_cons - nectar_se,
                      ymax = nectar_cons + nectar_se,
                      color = treatment)) +
  geom_smooth(mapping = aes(x = date,
                            y = nectar_cons,
                            color = treatment), se = FALSE) +
  theme_black()
```

#### Cumulative pollen consumption grouped by treatment
```{r}
  mc1.feed.df %>%
  group_by(id) %>%
  mutate(cum_pollen = cumsum(p_mass_cons_avg), 
         cum_nectar = cumsum(n_mass_cons)) %>%
  group_by(date, treatment) %>%
  summarise(nectar_cons = mean(cum_nectar), 
            nectar_se = (sd(cum_nectar) / (sqrt(n()))), 
            pollen_cons = mean(cum_pollen, na.rm = TRUE), 
            pollen_se = (sd(cum_pollen, na.rm = TRUE) / (sqrt(n())))) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = date,
                                y = pollen_cons,
                                ymin = pollen_cons - pollen_se,
                                ymax = pollen_cons + pollen_se,
                                color = treatment)) +
  geom_smooth(mapping = aes(x = date,
                            y = pollen_cons,
                            color = treatment), se = FALSE) +
  theme_black()
```

#### Calculate average interval mass gain across entire experiment
```{r}
mc.massgain <- mc1.df %>%
  select(id, date, mc_mass, p_mass_rm, p_mass_fd, treatment, mass_box) %>%
  mutate(p_mass_cons = mc1.feed.df$p_mass_cons_avg) %>%
  replace_na(list(mc_mass = 0)) %>%
  mutate(mc_mass_diff = c(0, diff(mc1.df$mc_mass))) %>%
  #filter(id == "3.3") %>%
  mutate(mc_mass_gain = ifelse(lag(!is.na(p_mass_rm == TRUE)), 
                               mc_mass_diff + lag(p_mass_rm) - lag(p_mass_fd) + p_mass_cons, 
                               mc_mass_diff - lag(p_mass_fd) + p_mass_cons)) # this needs to be checked...

mc.massgain$mc_mass_gain[which(diff(mc.massgain$id) != 0) + 1] <- NA
```

##### Average interval mass gain - z-score diverging dot plot
```{r}
mc.massgain %>% 
  group_by(id, treatment) %>%
  summarise(mean_intv_massgain = mean(mc_mass_gain, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(mass_gain_z = round((mean_intv_massgain - mean(mean_intv_massgain, na.rm = TRUE)) / sd(mean_intv_massgain, na.rm = TRUE), digits = 2)) %>%
  mutate(mass_score = ifelse(mass_gain_z < 0, 
                             "below", 
                             "above")) %>%
  arrange(desc(mass_gain_z)) %>%
  mutate(z_order = factor(`id`, 
                          levels = `id`)) %>%
  ggplot(aes(x = z_order, 
             y = mass_gain_z, 
             label = mass_gain_z)) + 
  geom_segment(mapping = aes(y = 0,
                             x = z_order,
                             yend = mass_gain_z,
                             xend = z_order),
               size = 1.1,
               color = "white",
               alpha = 0.25) + 
  geom_hline(yintercept = 0,
             linetype = "dashed",
             color = "red",
             size = 1.25,
             alpha = 0.25) +
  geom_point(stat = "identity", 
             mapping = aes(col = mass_score), 
             size = 8,
             alpha = 0.5) + 
  scale_color_manual(name = "Avg interval mass gain", 
                     labels = c("Above Average", 
                                "Below Average"),
                     values = c("above" = "green2", 
                                "below" = "red2")) + 
  geom_text(color = "white", 
            size = 2) + 
  labs(y = "Mass Gain Z-Score", 
       x = "Microcolony ID") + 
  coord_flip() + 
  theme_black()
```

##### Average interval mass gain - raw mass diverging dot plot
```{r}
mc.massgain %>% 
  group_by(id, treatment) %>%
  summarise(mean_intv_massgain = round(mean(mc_mass_gain, na.rm = TRUE), digits = 2)) %>%
  ungroup() %>%
  mutate(mass_score = ifelse(mean_intv_massgain < 0, 
                             "below", 
                             "above")) %>%
  arrange(desc(mean_intv_massgain)) %>%
  mutate(mass_order = factor(`id`, 
                             levels = `id`)) %>%
  ggplot(aes(x = mass_order, 
             y = mean_intv_massgain, 
             label = mean_intv_massgain)) + 
  geom_segment(mapping = aes(y = 0,
                             x = mass_order,
                             yend = mean_intv_massgain,
                             xend = mass_order),
               size = 1.1,
               color = "white",
               alpha = 0.25) + 
  geom_point(stat = "identity", 
             mapping = aes(col = mass_score), 
             size = 8,
             alpha = 0.5) + 
  scale_color_manual(name = "Average mass change", 
                     labels = c("Gained Mass", 
                                "Lost Mass"),
                     values = c("above" = "green2", 
                                "below" = "red2")) + 
  geom_text(color = "white", 
            size = 2) + 
  labs(y = "Mean feeding interval mass gain", 
       x = "Microcolony ID") + 
  coord_flip() + 
  theme_black()
```


## Round 2 Summary Plots 
#### Final comb mass
```{r}
mc2.end.df %>%
  filter(!is.na(end_mass_comb)) %>%
  group_by(treatment) %>%
  summarise(mean.comb.mass = mean(end_mass_comb), 
            se = sd(end_mass_comb) / sqrt(n())) %>%
  ggplot() + 
  geom_col(mapping = aes(x = treatment, 
                         y = mean.comb.mass, 
                         fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(x = treatment, 
                                y = mean.comb.mass,
                                ymax = mean.comb.mass + se, 
                                ymin = mean.comb.mass - se),
                  color = "white") +
  scale_y_continuous(limits = c(0, 10)) + 
  theme_black()
```
#### Corrected mass time series
```{r}
ggplot() + 
  geom_line(data = mc2.feed.df, mapping = aes(x = date, 
                                              y = mc_mass_true, 
                                              group = id, 
                                              color = treatment),
            size = 1.1) + 
  theme_black()
```

#### Total drones produced as point range
```{r}
mc2.drone.df %>%
  group_by(treatment) %>%
  summarise(mean_drones = mean(total_drones),
            sd_drones = sd(total_drones),
            se_drones = sd_drones / sqrt(7)) %>%
  ggplot() + 
  geom_col(mapping = aes(x = treatment,
                         y = mean_drones,
                         fill = treatment,
                         width = 0.5)) + 
    geom_pointrange(mapping = aes(x = treatment, 
                                y = mean_drones, 
                                ymax = mean_drones + se_drones,
                                ymin = mean_drones - se_drones),
                  color = "white") + 
  theme_black()
```

#### Total drones produced as boxplot
```{r}
mc2.df %>%
  group_by(id, treatment) %>%
  summarise(total_drones = sum(n_new_drones, na.rm = TRUE)) %>%
  ggplot(mapping = aes(x = treatment,
                       y = total_drones)) +
  geom_boxplot(mapping = aes(fill = treatment),
               color = "white") +
  theme_black()

```

#### Drone production normalized across MC - diverging dot plot
```{r}
mc2.df %>%
  group_by(id, treatment) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(drone_z = round((total_males - mean(total_males, na.rm = TRUE)) / sd(total_males, na.rm = TRUE), digits = 2)) %>%
  mutate(drone_score = ifelse(drone_z < 0, "below", "above")) %>%
  arrange(desc(drone_z)) %>%
  mutate(z_order = factor(`id`, 
                          levels = `id`)) %>%
  ggplot(aes(x = z_order, 
             y = drone_z, 
             label = drone_z)) + 
  geom_segment(mapping = aes(y = 0,
                             x = z_order,
                             yend = drone_z,
                             xend = z_order),
               size = 1.1,
               color = "white",
               alpha = 0.25) + 
  geom_point(stat = "identity", 
             mapping = aes(col = drone_score), 
             size = 8,
             alpha = 0.5) +
    geom_hline(yintercept = 0,
             color = "red",
             size = 0.5,
             alpha = 0.35) +
  scale_color_manual(name = "Drone Production", 
                     labels = c("Above Average", "Below Average"),
                     values = c("above" = "green2", "below" = "red2")) + 
  geom_text(color = "white",
            size = 2) + 
  labs(y = "Drone Production Z-Score", 
       x = "Microcolony ID") + 
  coord_flip() + 
  theme_black() 
```

#### Average mass gain - smoothed
```{r}
ggplot() + 
  geom_smooth(data = mc2.feed.df,
              mapping = aes(x = date, 
                            y = mc_mass_true,
                            color = treatment,
                            fill = treatment),
              method = "loess") + 
  theme_black()
```

#### Cumulative nectar consumption
```{r}
mc2.feed.df %>%
  ungroup() %>%
  group_by(id) %>%
  filter(!is.na(p_mass_cons_avg)) %>%
  mutate(cum_pollen = cumsum(p_mass_cons_avg), 
         cum_nectar = cumsum(n_mass_cons)) %>%
  group_by(date, treatment) %>%
  summarise(nectar_cons = mean(cum_nectar), 
            nectar_se = (sd(cum_nectar) / (sqrt(n()))), 
            pollen_cons = mean(cum_pollen, na.rm = TRUE), 
            pollen_se = (sd(cum_pollen, na.rm = TRUE) / (sqrt(n())))) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = date,
                                y = nectar_cons,
                                ymin = nectar_cons - nectar_se,
                                ymax = nectar_cons + nectar_se,
                                color = treatment),
                  na.rm = TRUE) +
  geom_smooth(mapping = aes(x = date,
                            y = nectar_cons,
                            color = treatment), se = FALSE) +
  theme_black()
```

#### Cumulative pollen consumption grouped by treatment
```{r}
  mc2.feed.df %>%
  group_by(id) %>%
  filter(!is.na(p_mass_cons_avg)) %>%
  mutate(cum_pollen = cumsum(p_mass_cons_avg), 
         cum_nectar = cumsum(n_mass_cons)) %>%
  group_by(date, treatment) %>%
  summarise(nectar_cons = mean(cum_nectar), 
            nectar_se = (sd(cum_nectar) / (sqrt(n()))), 
            pollen_cons = mean(cum_pollen, na.rm = TRUE), 
            pollen_se = (sd(cum_pollen, na.rm = TRUE) / (sqrt(n())))) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = date,
                                y = pollen_cons,
                                ymin = pollen_cons - pollen_se,
                                ymax = pollen_cons + pollen_se,
                                color = treatment)) +
  geom_smooth(mapping = aes(x = date,
                            y = pollen_cons,
                            color = treatment), se = FALSE) +
  theme_black()
```

#### Calculate average interval mass gain
##### Average interval mass gain - z-score normalized
```{r}
mc2.feed.df %>% 
  group_by(id, treatment) %>%
  summarise(mean_intv_massdiff = mean(mc_mass_diff, 
                                      na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(mass_diff_z = round((mean_intv_massdiff - mean(mean_intv_massdiff, na.rm = TRUE)) / sd(mean_intv_massdiff,                                                                                                          na.rm = TRUE), 
                             digits = 2)) %>%
  mutate(mass_score = ifelse(mass_diff_z < 0, 
                             "below", 
                             "above")) %>%
  arrange(desc(mass_diff_z)) %>%
  mutate(z_order = factor(`id`, 
                          levels = `id`)) %>%
  ggplot(aes(x = z_order, 
             y = mass_diff_z, 
             label = mass_diff_z)) + 
  geom_segment(mapping = aes(y = 0,
                             x = z_order,
                             yend = mass_diff_z,
                             xend = z_order),
               size = 1.1,
               color = "white",
               alpha = 0.25) + 
  geom_hline(yintercept = 0,
             linetype = "dashed",
             color = "red",
             size = 1.25,
             alpha = 0.25) +
  geom_point(stat = "identity", 
             mapping = aes(col = mass_score), 
             size = 8,
             alpha = 0.5) + 
  scale_color_manual(name = "Mean interval mass difference", 
                     labels = c("Above Average", 
                                "Below Average"),
                     values = c("above" = "green2", 
                                "below" = "red2")) + 
  geom_text(color = "white", 
            size = 2) + 
  labs(y = "Mass Difference Z-Score", 
       x = "Microcolony ID") + 
  coord_flip() + 
  theme_black()
```

#### Drone production bump chart - by treatment
```{r}

mc2.df$id <- as.factor(mc2.df$id)
mc2.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(fd.day = row_number()) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  arrange(id, date) %>%
  ggplot(mapping = aes(x = fd.day,
                       y = csum_drones,
                       group = id)) + 
  geom_line(mapping = aes(color = treatment), 
            alpha = 0.6,
            size = 1.5) + 
  geom_point(mapping = aes(color = treatment),
             alpha = 0.75,
             size = 3) + 
  annotate("rect",
           xmin = 4,
           xmax = 6,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  annotate("rect",
           xmin = 11,
           xmax = 13,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
    scale_x_continuous(breaks = unique(mc2.df$fd.day)) +
  labs(y = "Cumulative Drone Production",
       x = "Feeding Interval") + 
  theme_black()

```