---
title: "2018 Bumble Bee Microcolony Experiment"
output: html_notebook 
date: "1/31/19"
subtitle: "Summary figures - Round 3"
---
**Name:** Jeremy Hemberger
**Email:** j.hemberger.wisc@gmail.com
**Institution:** University of Wisconsin - Madison | Department of Entomology

## Load packages
```{r}
library(tidyverse)
library(lubridate)
library(broom)
library(plyr)
```

### Final comb mass
```{r}
mc3.end.df %>%
  group_by(treatment) %>%
  dplyr::summarise(mean.comb.mass = mean(end_mass_comb), 
                   se = sd(end_mass_comb) / sqrt(n())) %>%
  ggplot() + 
  geom_col(mapping = aes(x = treatment, 
                         y = mean.comb.mass, 
                         fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(x = treatment, 
                                y = mean.comb.mass,
                                ymax = mean.comb.mass + se, 
                                ymin = mean.comb.mass - se),
                  color = "white") +
  scale_y_continuous(limits = c(0, 10)) + 
  theme_black()
```

### Raw mass gain for all microcolony replicates
```{r}
mc3.feed.df %>%
  filter(!is.na(mc_mass_true)) %>%
  ggplot(na.rm = TRUE) + 
  geom_line(mapping = aes(x = fd.day, 
                          y = mc_mass_true, 
                          group = id, 
                          color = treatment),
            na.rm = TRUE,
            size = 1.1) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  scale_x_continuous(breaks = unique(mc3.feed.df$fd.day)) + 
  theme_black()
```

### Drone production
#### Total drone production: bar 
```{r}
mc3.df %>%
  filter(id != 2.7) %>%
  group_by(id, treatment) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  group_by(treatment) %>%
  summarise(mean_males = mean(total_males), 
            se = sd(total_males) / sqrt(n())) %>%
  ggplot() + 
  geom_col(mapping = aes(x = treatment,
                         y = mean_males,
                         fill = treatment,
                         width = 0.5)) + 
  geom_pointrange(mapping = aes(x = treatment, 
                                y = mean_males, 
                                ymax = mean_males + se,
                                ymin = mean_males - se),
                  color = "white") + 
  theme_black()
```

#### Total drone production: box
```{r}
mc3.df %>%
  filter(id != 2.7) %>%
  group_by(id, treatment) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  group_by(treatment) %>%
  ggplot(mapping = aes(x = treatment, 
                       y = total_males)) + 
  geom_boxplot(mapping = aes(fill = treatment),
               color = "white") + 
  theme_black()
```

#### Drone production: diverging dot
```{r}
mc3.df %>%
  filter(id != 2.7) %>%
  group_by(id, treatment) %>%
  summarise(total_males = sum(n_new_drones, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(drone_z = round((total_males - mean(total_males, na.rm = TRUE)) / sd(total_males, na.rm = TRUE), digits = 2)) %>%
  mutate(drone_score = ifelse(drone_z < 0, "below", "above")) %>%
  arrange(desc(drone_z)) %>%
  mutate(z_order = factor(`id`, 
                          levels = `id`)) %>%
  ggplot(aes(x = z_order, 
             y = drone_z, 
             label = drone_z)) + 
  geom_segment(mapping = aes(y = 0,
                             x = z_order,
                             yend = drone_z,
                             xend = z_order),
               size = 1.1,
               color = "white",
               alpha = 0.25) + 
  geom_point(stat = "identity", 
             mapping = aes(col = drone_score), 
             size = 8,
             alpha = 0.5) + 
  scale_color_manual(name = "Drone Production", 
                     labels = c("Above Average", "Below Average"),
                     values = c("above" = "green2", "below" = "red2")) + 
  geom_text(color = "white",
            size = 2) + 
  labs(y = "Drone Production Z-Score", 
       x = "Microcolony ID") + 
  coord_flip() + 
  theme_black() 
```

#### Drone production bump chart - by treatment
```{r}
mc3.df$id <- as.factor(mc3.df$id)
mc3.df %>%
  filter(id != 2.7) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(fd.day = row_number()) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>% # won't work unless NO NA's
  arrange(id, date) %>%
  ggplot(mapping = aes(x = fd.day,
                       y = csum_drones,
                       group = id)) + 
  geom_line(mapping = aes(color = treatment), 
            alpha = 0.6,
            size = 1.5) + 
  geom_point(mapping = aes(color = treatment),
             alpha = 0.75,
             size = 3) + 
  annotate("rect",
           xmin = 4,
           xmax = 6,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  annotate("rect",
           xmin = 11,
           xmax = 13,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  scale_x_continuous(breaks = unique(mc3.df$fd.day)) +
  labs(y = "Cumulative Drone Production",
       x = "Feeding Interval") + 
  theme_black()
```

```{r}
mc3.df %>%
  dplyr::filter(id != 2.7) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(id, treatment) %>%
  dplyr::mutate(fd.day = row_number()) %>%
  dplyr::mutate(csum_drones = cumsum(n_new_drones)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(treatment, date, fd.day) %>%
  dplyr::summarise(mean_csum_drones = mean(csum_drones)) %>%
  dplyr::arrange(treatment, date, fd.day) %>%
  ggplot(mapping = aes(x = fd.day,
                       y = mean_csum_drones,
                       group = treatment)) +
  geom_line(mapping = aes(color = treatment),
            alpha = 0.6,
            size = 1.5) +
  geom_point(mapping = aes(color = treatment),
             alpha = 0.75,
             size = 3) +
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) +
  scale_x_continuous(breaks = unique(mc3.df$fd.day)) +
  labs(y = "Cumulative Drone Production",
       x = "Feeding Interval") +
  theme_black()
```

### Mass Gain
#### Smoothed growth curve
```{r}
ggplot(data = mc3.feed.df) + 
  geom_smooth(span = 0.75, 
              mapping = aes(x = fd.day, 
                            y = mc_mass_true, #- mass_box - lag(p_mass_fd),
                            color = treatment,
                            fill = treatment),
              method = "loess") + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "white",
           alpha = 0.2) + 
  scale_x_continuous(breaks = unique(mc3.feed.df$fd.day)) + 
  theme_black()
```

### Cumulative nectar consumption: by treatment
```{r}
mc3.feed.df %>%
  dplyr::group_by(id) %>%
  filter(!is.na(p_mass_cons_avg),
         !is.na(n_mass_cons)) %>%
  dplyr::mutate(cum_pollen = cumsum(p_mass_cons_avg), 
                cum_nectar = cumsum(n_mass_cons)) %>%
  dplyr::group_by(date, treatment) %>%
  dplyr::summarise(nectar_cons = mean(cum_nectar), 
                   nectar_se = (sd(cum_nectar) / (sqrt(n()))), 
                   pollen_cons = mean(cum_pollen, na.rm = TRUE), 
                   pollen_se = (sd(cum_pollen, na.rm = TRUE) / (sqrt(n())))) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = date,
                      y = nectar_cons,
                      ymin = nectar_cons - nectar_se,
                      ymax = nectar_cons + nectar_se,
                      color = treatment)) +
  geom_smooth(mapping = aes(x = date,
                            y = nectar_cons,
                            color = treatment), se = FALSE) +
  theme_black()
```

### Cumulative pollen consumption: by treatment
```{r}
  mc3.feed.df %>%
  filter(!is.na(p_mass_cons_avg)) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(cum_pollen = cumsum(p_mass_cons_avg), 
                cum_nectar = cumsum(n_mass_cons)) %>%
  dplyr::group_by(date, treatment) %>%
  dplyr::summarise(nectar_cons = mean(cum_nectar), 
            nectar_se = (sd(cum_nectar) / (sqrt(n()))), 
            pollen_cons = mean(cum_pollen, na.rm = TRUE), 
            pollen_se = (sd(cum_pollen, na.rm = TRUE) / (sqrt(n())))) %>%
  ggplot() +
  geom_pointrange(mapping = aes(x = date,
                                y = pollen_cons,
                                ymin = pollen_cons - pollen_se,
                                ymax = pollen_cons + pollen_se,
                                color = treatment)) +
  geom_smooth(mapping = aes(x = date,
                            y = pollen_cons,
                            color = treatment), se = FALSE) +
  theme_black()
```

### Drone fitness

### Worker mortality
```{r}
mc3.df %>%
  dplyr::group_by(id, treatment) %>%
  dplyr::filter(id != 2.7) %>%
  dplyr::summarise(total_worker_death = sum(n_worker_deaths, na.rm = TRUE)) %>%
  dplyr::group_by(treatment) %>%
  dplyr::summarise(mean_worker_death = mean(total_worker_death), 
                   se = sd(total_worker_death) / sqrt(n())) %>%
  ggplot() + 
    geom_col(mapping = aes(x = treatment,
                           y = mean_worker_death,
                           fill = treatment,
                           width = 0.5)) + 
  geom_pointrange(mapping = aes(x = treatment, y = mean_worker_death, 
                                ymax = mean_worker_death + se,
                                ymin = mean_worker_death - se),
                  color = "white") + 
  theme_black()
```

### Time to maturity/drone production
```{r}
mc3.df %>%
  dplyr::filter(id != 2.7) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(id, treatment) %>%
  dplyr::mutate(index_to_drone = min(which(n_new_drones > 0)),
                date_to_drone = date[index_to_drone]) %>%
  dplyr::select(date, id, treatment, index_to_drone, date_to_drone) %>%
  dplyr::mutate(days_to_drone = (as.duration(ymd("2018-11-10") %--% date_to_drone) / 86400)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(treatment) %>%
  dplyr::summarise(mean_days_to_drone = mean(days_to_drone, na.rm = TRUE),
                   se = sd(days_to_drone, na.rm = TRUE) / sqrt(n())) %>%
  ggplot(mapping = aes(x = treatment,
                       y = mean_days_to_drone)) + 
  geom_col(fill = "indianred1",
           width = 0.5) + 
  geom_pointrange(mapping = aes(ymax = mean_days_to_drone + se,
                                ymin = mean_days_to_drone - se),
                  color = "white") + 
  labs(y = "Mean Days to Drone Production",
       x = "Treatment") + 
  theme_black()
```

### Rate of microcolony growth
#### Zone 1
```{r}
mc3.feed.df$pulse_cat <- as.character(mc3.feed.df$pulse_cat)
mc3.feed.df %>%
  ungroup() %>%
  filter(treatment == "zone.1") %>%
  ggplot() + 
  geom_point(mapping = aes(x = fd.day,
                           y = mc_mass_true,
                           color = pulse_cat)) + 
  geom_smooth(mapping = aes(x = fd.day,
                            y = mc_mass_true,
                            col = pulse_cat),
              method = "lm",
              se = FALSE) + 
  scale_x_continuous(breaks = unique(mc3.feed.df$fd.day)) + 
  theme_black()

```
#### Zone 2

#### Zone 3

#### Zone 4

#### Avg. growth by time
```{r}
trt.slopes <- function() {
  trts <- unique(mc3.feed.df$treatment)
  df.ls <- list() 
  for (i in trts) {
    df <- mc3.feed.df %>%
      filter(treatment == i) %>%
      plyr::dlply("pulse_cat", function(.)
                  tidy(lm(mc_mass_true ~ fd.day, data = .))) %>%
      bind_rows(.id = "id") %>%
      mutate(treatment = i)
    df.ls[[i]] <- df
  }
  df.end <- bind_rows(df.ls)
  assign("mc3.trtslope.df",
         df.end,
         envir = .GlobalEnv)
}
trt.slopes()
mc3.trtslope.df
```

```{r}
mc3.trtslope.df$id <- as.factor(mc3.trtslope.df$id)
mc3.trtslope.df$id <- factor(mc3.trtslope.df$id, levels = c("b1",
                                                            "p1",
                                                            "a1.b2",
                                                            "p2",
                                                            "a2"))
mc3.trtslope.df %>%
  filter(term != "(Intercept)") %>%
  ggplot() + 
  geom_pointrange(mapping = aes(x = id,
                                y = estimate,
                                ymin = estimate - std.error,
                                ymax = estimate + std.error,
                                color = treatment),
                  size = 1) + 
  geom_line(mapping = aes(x = id,
                           y = estimate,
                           group = treatment,
                           color = treatment),
            size = 1.25,
            alpha = 0.75) + 
  geom_hline(yintercept = 0,
             color = "white",
             size = 1.25,
             alpha = 0.25) + 
  labs(x = "Period relative to food pulse",
       y = "Estimated rate of mass gain") + 
  scale_y_continuous(limits = c(-3, 3),
                     breaks = seq(-3, 3, by = 1)) + 
  theme_black()
```

