---
title: "2018 Resource Pulse Microcolony Analysis - All Rounds Combined"
subtitle: Analysis and model construction/selection
date: "2/7/2018"
output: html_notebook
---

**Name:** Jeremy Hemberger
**Email:** j.hemberger.wisc@gmail.com
**Institution:** University of Wisconsin - Madison | Department of Entomology

### Import packages 
```{r echo = TRUE, results = "hide"}
library(psych)
library(nlme) #lmer can't use temporal corrleation structures
library(car)
library(multcompView)
library(lsmeans)
library(tidyverse)
library(rcompanion)
library(lmtest)
library(gam)
library(gamm4)
library(mgcv)
library(knitr)
library(lubridate)
library(broom)
library(svglite)
```

## Load in data
```{r}
mc1.df <- read_csv("./D2018_MicroCol_Round1_Clean.csv")
mc1.feed.df <- read_csv("./D2018_MicroCol_Round1_Feed_Clean.csv")
mc1.drone.df <- read_csv("./D2018_microcol_round3_drone.csv")
mc1.drone.it.df <- 
mc2.drone.mass.df <- 

mc2.df <- read_csv("./D2018_MicroCol_Round1_Clean.csv")
mc2.feed.df <- read_csv("./D2018_MicroCol_Round1_Feed_Clean.csv")
mc2.drone.df <- read_csv("./D2018_microcol_round3_drone.csv")
mc2.drone.it.df <- read_csv()
mc2.drone.mass.df <- read_csv()

mc3.df <- read_csv("./D2018_microcol_round3_clean.csv")
mc3.end.df <- read_csv("./D2018_MicroCol_Round3_BroodMass.csv")
mc3.feed.df <- read_csv("./D2018_microcol_round3_feed_clean.csv")
mc3.drone.df <- read_csv("./D2018_microcol_round3_drone.csv")
mc3.drone.it.df <- read_csv()
mc3.drone.mass.df <- read_csv() 
```

### Adjust `mc1.feed.df` to match 
```{r}
mc1.feed.mod.df <- mc1.feed.df
mc1.feed.mod.df$fd.day.count <- NULL
mc1.feed.mod.df$mc_mass_true <- NULL
names(mc1.feed.mod.df)[names(mc1.feed.mod.df) == "mc_mass_true_intrp"] <- "mc_mass_true"
mc1.feed.mod.df <- mc1.feed.mod.df %>%
  select(-pulse_cat, pulse_cat)
names(mc1.feed.mod.df) == names(mc2.feed.df)
names(mc2.feed.df) == names(mc3.feed.df)
mc1.feed.mod.df$id <- as.character(mc1.feed.mod.df$id)
mc2.feed.df$id <- as.character(mc2.feed.df$id)
mc3.feed.df$id <- as.character(mc3.feed.df$id)

mc1.feed.mod.df$id <- as.factor(mc1.feed.mod.df$id)
mc2.feed.df$id <- as.factor(mc2.feed.df$id)
mc3.feed.df$id <- as.factor(mc3.feed.df$id)
```


## Combine data
```{r}
mc.all.df <- bind_rows(mc1.df,
                       mc2.df,
                       mc3.df,
                       .id = "rep") # end up doing on fly with specific columns
mc.feed.all.df <- bind_rows(mc1.feed.df,
                            mc2.feed.df,
                            mc3.feed.df,
                            .id = "rep")
mc.feed.all.df$id <- as.character(mc.feed.all.df$id)
mc.feed.all.df$id <- as.factor(mc.feed.all.df$id)
mc.drone.all.df <- bind_rows(mc1.drone.df,
                             mc2.drone.df,
                             mc3.drone.df,
                             .id = "rep") 
# mc.drone.it.all.df <- bind_rows()
# mc.drone.mass.all.df <- bind_rows()

mc.feed.all.df <- mc.feed.all.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(mc_mass_true = na.approx(mc_mass_true, 
                                  maxgap = 4,
                                  rule = 2))
```



## RM ANOVA on mass gain
#### Temporal correlation structure
```{r}
mcall.mass.model = lme(mc_mass_true ~ treatment + rep + date + treatment * date,
                       random = ~ 1 | id,
                       data = mc.feed.all.df,
                       na.action = na.exclude)
ACF(mcall.mass.model)
acf(mc.feed.all.df$mc_mass_true, 
    na.action = na.exclude)
```

#### Full model
```{r}
mcall.mass.model.1 = lme(mc_mass_true ~ treatment + rep + date + treatment*date, 
                         random = ~ 1 | id,
                         data = mc.feed.all.df,
                         correlation = corAR1(form = ~ date | id,
                                              value = 0.304686),
                         na.action = na.exclude,
                         method = "REML")
Anova(mcall.mass.model.1)
tidy(mcall.mass.model.1)
anova(mcall.mass.model.1)
summary(mcall.mass.model.1)
```

#### Fixed effects only w/comparison
```{r}
mcall.mass.model.1.fixed <- gls(mc_mass_true ~ treatment + date + treatment*date,
                                data = mc.feed.all.df,
                                method = "REML",
                                na.action = na.exclude)
anova(mcall.mass.model.1, mcall.mass.model.1.fixed)
```

```{r}

```


#### Null model w/comparison
```{r}
mcall.mass.model.null <- lme(mc_mass_true ~ 1,
                             random = ~ 1 | id,
                             data = mc.feed.all.df,
                             na.action = na.exclude)
nagelkerke(mcall.mass.model.1,
           mcall.mass.model.null)
```

#### Groupwise estimated means
```{r}
mcall.mass.gwm.df <- groupwiseMean(mc_mass_true ~ treatment + fd_day,
                                   data = mc.feed.all.df,
                                   conf = 0.95,
                                   digits = 3)
mcall.mass.gwm.df
```

#### Plot groupwise means
```{r}
mcall.mass.gwm.df %>%
  ungroup() %>%
  group_by(treatment) %>%
  mutate(Mean = na.approx(Mean, 
                          maxgap = 4,
                          rule = 2)) %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
ggplot(mapping = aes(x = fd_day,
                     y = Mean,
                     group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean mass") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(mcall.mass.gwm.df$fd_day)) + 
  scale_y_continuous(limits = c(0, 10.5)) + 
  ggsave("mean_mass_fitted.eps")
```


#### Model diagnostics 
```{r}
plotNormalHistogram(residuals(mcall.mass.model.1))
plot(residuals(mcall.mass.model.1),
     fitted(mcall.mass.model.1))
plot(residuals(mcall.mass.model.1))
acf(residuals(mcall.mass.model.1),
    na.action = na.exclude)
```



## LMM on brood mass
#### Model specification
```{r}
mcall.brood.lmm <- lme(end_mass_comb ~ treatment + round,
                       random = ~ 1 | id,
                       data = mc.end.all.df,
                       na.action = na.exclude)
tidy(mcall.brood.lmm)
summary(mcall.brood.lmm)
anova(mcall.brood.lmm)

plotNormalHistogram(residuals(mcall.brood.lmm))
plot(residuals(mcall.brood.lmm),
     fitted(mcall.brood.lmm))
plotNormalHistogram(mc.end.all.df$end_mass_comb)
plot(mcall.brood.lmm, which = 1 :4)
```

#### LS means Calculation
```{r}
mcall.brood.marginal <- lsmeans(mcall.brood.lmm, ~ treatment)
mcall.brood.cld <- cld(mcall.brood.marginal,
                       alpha = 0.05,
                       Letters = letters,
                       adjust = "tukey")
mcall.brood.cld
```

#### Plot LS means
```{r}
mcall.brood.cld$.group=gsub(" ", "", mcall.brood.cld$.group)
ggplot(data = mcall.brood.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 0.5),
             color = "black") + 
  scale_y_continuous(limits = c(0, 10),
                     expand = c(0, 0)) +
  ylab("Least square mean brood mass") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1)) +
  ggsave("mean_broodmass_fitted.eps")
```



## RM ANOVA on drone production

#### Bump chart for cumulative drone production 
##### Re-make `mc.drone.all.df` tibble 
```{r}
mc.drone.all.df <- bind_rows(mc1.df %>%
  group_by(id) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  select(id, treatment, fd_day, csum_drones), 
  mc2.df %>%
  group_by(id) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  select(id, treatment, fd_day, csum_drones),
  mc3.df %>%
  group_by(id) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  select(id, treatment, fd_day, csum_drones), 
  .id = "rep") 
```

##### Plot bumpchart
```{r}
mc.drone.all.df %>%
  group_by(treatment, fd_day) %>%
  summarise(mean_csum_drones = round(mean(csum_drones, na.rm = TRUE)),
            se_mean_csum_drones = sd(csum_drones, na.rm = TRUE) / sqrt(n())) %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", "constant", 
                          ifelse(treatment == "zone.2", "constant", "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = mean_csum_drones,
                       group = treatment)) +
  geom_errorbar(mapping = aes(ymin = mean_csum_drones - se_mean_csum_drones,
                              ymax = mean_csum_drones + se_mean_csum_drones),
                size = 0.7,
                width = 0,
                color = "black") + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  geom_point(mapping = aes(color = treatment),
             alpha = 1,
             size = 3) +
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                     name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  scale_x_continuous(breaks = unique(mc.drone.all.df$fd_day)) +
  facet_grid(rows = vars(trt_cat)) + 
  labs(y = "Cumulative Drone Production",
       x = "Feeding Interval") + 
  ggsave("mean_drone_bump_fitted.eps")
```

## LMM on total drone production
#### Model specification 
```{r}
mcall.drone.lmm <- lme(total_drones ~ treatment + rep,
                       random = ~ 1 | id,
                       data = mc.drone.all.df,
                       na.action = na.exclude)
tidy(mcall.drone.lmm)
summary(mcall.drone.lmm)
anova(mcall.drone.lmm)

plotNormalHistogram(mcall.drone.lmm.resid)
plot(residuals(mcall.drone.lmm),
     fitted(mcall.drone.lmm))
plotNormalHistogram(mc.drone.all.df$total_drones) # May be better off with log transforming resp. 
```

#### LS means Calculation
```{r}
mcall.drone.marginal <- lsmeans(mcall.drone.lmm, ~ treatment)
mcall.drone.cld <- cld(mcall.drone.marginal,
                       alpha = 0.05,
                       Letters = letters,
                       adjust = "tukey")
mcall.drone.cld
```

#### Plot LS means
```{r}
mcall.drone.cld$.group=gsub(" ", "", mcall.drone.cld$.group)
ggplot(data = mcall.drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "black") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "none") +
  geom_text(mapping = aes(y = upper.CL + 1.5),
             color = "black") + 
  scale_y_continuous(limits = c(0, 25),
                     expand = c(0, 0)) +
  ylab("Least square mean drone production") + 
  xlab("Treatment") +
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") +
  ggsave("mean_drone_fitted.eps")
```


## LMM for days to first drone
#### Gather data
```{r}
mc.all.t2drone.df <- bind_rows(
  select(mc1.df, 
         id, 
         treatment, 
         date, 
         n_new_drones, 
         fd_day),
  select(mc2.df,
         id,
         treatment,
         date,
         n_new_drones,
         fd_day), 
  select(mc3.df,
         id,
         treatment,
         date,
         n_new_drones,
         fd_day),
  .id = "rep")

mc.all.t2drone.df <- mc.all.t2drone.df %>%
  group_by(id, rep, treatment) %>%
  mutate(csum_drones = cumsum(n_new_drones)) %>%
  mutate(start_date = first(date)) %>%
  group_by(id, rep, treatment, start_date) %>%
  summarise(index_to_drone = min(which(csum_drones > 0)),
            date_to_drone = date[index_to_drone]) %>%
  mutate(days_to_drone = (as.duration(ymd(start_date) %--% date_to_drone / 86400))) %>%
  filter(!is.na(days_to_drone))
```

#### Model specification
```{r}
mcall.t2drone.lmm <- lme(days_to_drone ~ treatment + rep,
                         random = ~ 1 | id,
                         data = mc.all.t2drone.df,
                         na.action = na.exclude)
tidy(mcall.t2drone.lmm)
summary(mcall.t2drone.lmm)
anova(mcall.t2drone.lmm)

plotNormalHistogram(residuals(mcall.t2drone.lmm))
plot(residuals(mcall.t2drone.lmm),
     fitted(mcall.t2drone.lmm))
plotNormalHistogram(mc.all.t2drone.df$days_to_drone)
```

#### LS means Calculation
```{r}
mcall.t2drone.marginal <- lsmeans(mcall.t2drone.lmm, ~ treatment)
mcall.t2drone.cld <- cld(mcall.t2drone.marginal,
                         alpha = 0.05,
                         Letters = letters,
                         adjust = "tukey")
mcall.t2drone.cld
```

#### Plot LS means
```{r}
mcall.t2drone.cld$.group=gsub(" ", "", mcall.t2drone.cld$.group)
ggplot(data = mcall.t2drone.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 2),
             color = "black") + 
  scale_y_continuous(limits = c(0, 35),
                     expand = c(0, 0)) +
  ylab("Least square mean days to first drone") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1)) + 
  ggsave("mean_t2drone_fitted.eps")
```

## LMM for worker mortality 
#### Gather data
```{r}
mc.all.work.df <- bind_rows(
  select(mc1.df, 
         id, 
         treatment, 
         date, 
         n_worker_deaths, 
         fd_day),
  select(mc2.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day), 
  select(mc3.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day),
  .id = "rep")

mc.all.work.df <- mc.all.work.df %>%
  group_by(id, rep, treatment) %>%
  summarise(total_worker_deaths = sum(n_worker_deaths))
```

#### Model specification
```{r}
mcall.work.lmm <- lme(total_worker_deaths ~ treatment + rep,
                         random = ~ 1 | id,
                         data = mc.all.work.df,
                         na.action = na.exclude)

tidy(mcall.work.lmm)
summary(mcall.work.lmm)
anova(mcall.work.lmm)

plotNormalHistogram(residuals(mcall.work.lmm))
plot(residuals(mcall.work.lmm),
     fitted(mcall.work.lmm))
plotNormalHistogram(mc.all.work.df$total_worker_deaths)
```

#### LS means Calculation
```{r}
mcall.work.marginal <- lsmeans(mcall.work.lmm, ~ treatment)
mcall.work.cld <- cld(mcall.work.marginal,
                         alpha = 0.05,
                         Letters = letters,
                         adjust = "tukey")
mcall.work.cld
```

#### Plot LS means
```{r}
mcall.work.cld$.group=gsub(" ", "", mcall.work.cld$.group)
ggplot(data = mcall.work.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "black") + 
  scale_y_continuous(limits = c(0, 20),
                     expand = c(0, 0)) +
  ylab("Least square mean worker mortality") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1)) + 
  ggsave("mean_work_fitted.eps")
```



## RM ANOVA on pollen/nectar consumption
#### Pollen
##### Gather data
```{r}
mc.feed.all.df$p_mass_cons[is.na(mc.feed.all.df$p_mass_cons)] <- 0
mc.feed.all.df$n_mass_cons[is.na(mc.feed.all.df$n_mass_cons)] <- 0
mc.feed.all.mod.df <- mc.feed.all.df %>%
  ungroup() %>%
  group_by(id, rep) %>%
  mutate(total_p_cons = cumsum(p_mass_cons_avg),
         total_n_cons = cumsum(n_mass_cons)) %>%
  filter(fd_day != 0)
```

##### Temporal correlation structure
```{r}
mcall.fcon.model = lme(total_p_cons ~ treatment + rep + date + treatment * date,
                       random = ~ 1 | id,
                       data = mc.feed.all.mod.df,
                       na.action = na.exclude)
ACF(mcall.fcon.model)
acf(mc.feed.all.df$total_p_cons, 
    na.action = na.exclude)
```

##### Full model
```{r}
mcall.fcon.model.1 = lme(total_p_cons ~ treatment + rep + date + treatment*date, 
                         random = ~ 1 | id,
                         data = mc.feed.all.mod.df,
                         correlation = corAR1(form = ~ date | id,
                                              value = 0.8981),
                         na.action = na.exclude,
                         method = "REML")
Anova(mcall.fcon.model.1)
anova(mcall.fcon.model.1)
summary(mcall.fcon.model.1)
```

##### Groupwise means
```{r}
mcall.fcon.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  total_p_cons ~ treatment + fd_day,
  data = mc.feed.all.mod.df,
  conf = 0.95,
  digits = 3
  )

mcall.fcon.gwm.df
```

##### Plot groupwise means
```{r}
mcall.fcon.gwm.df %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = Mean,
                       group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean cumulative pollen consumption") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(mcall.fcon.gwm.df$fd_day))
```


##### Model diagnostics 
```{r}
plotNormalHistogram(residuals(mcall.fcon.model.1))
plot(residuals(mcall.fcon.model.1),
     fitted(mcall.fcon.model.1))
plot(mcall.fcon.model.1)
plot(residuals(mcall.fcon.model.1))
acf(residuals(mcall.fcon.model.1))
```


##### Plotting raw summarised
```{r}
mc.feed.all.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(total_p_cons = cumsum(p_mass_cons_avg),
         total_n_cons = cumsum(n_mass_cons)) %>%
  group_by(fd_day, treatment) %>%
  summarise(nectar_cons = mean(total_n_cons), 
            nectar_se = (sd(total_n_cons) / (sqrt(n()))), 
            pollen_cons = mean(total_p_cons, na.rm = TRUE), 
            pollen_se = (sd(total_p_cons, na.rm = TRUE) / (sqrt(n())))) %>%
  filter(fd_day != 0) %>%
  ggplot() +
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_pointrange(mapping = aes(x = fd_day,
                                y = nectar_cons,
                                ymin = nectar_cons - nectar_se,
                                ymax = nectar_cons + nectar_se,
                                color = treatment),
                  size = 1.0) +
  geom_smooth(mapping = aes(x = fd_day,
                            y = nectar_cons,
                            color = treatment), 
              se = FALSE,
              size = 1.5) + 
  theme_microcol() + 
  ylab("Mean nectar consumption") + 
  xlab("Interval Feeding Day") + 
  scale_color_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.position = "nothing") + 
  scale_x_continuous(breaks = unique(mc.feed.all.df$fd_day)) + 
  ggsave("ncons.eps", width = 7, height = 3.5)
  
```


#### Nectar
##### Temporal correlation structure
```{r}
mcall.ncon.model = lme(total_n_cons ~ treatment + rep + date + treatment * date,
                       random = ~ 1 | id,
                       data = mc.feed.all.mod.df,
                       na.action = na.exclude)
ACF(mcall.ncon.model)
acf(mc.feed.all.mod.df$total_n_cons, 
    na.action = na.exclude)
```

##### Full model
```{r}
mcall.ncon.model.1 = lme(total_p_cons ~ treatment + rep + date + treatment*date, 
                         random = ~ 1 | id,
                         data = mc.feed.all.mod.df,
                         correlation = corAR1(form = ~ date | id,
                                              value = 0.84326),
                         na.action = na.exclude,
                         method = "REML")
Anova(mcall.ncon.model.1)
anova(mcall.ncon.model.1)
summary(mcall.ncon.model.1)
```

##### Groupwise means
```{r}
mcall.ncon.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  total_n_cons ~ treatment + fd_day,
  data = mc.feed.all.mod.df,
  conf = 0.95,
  digits = 3
  )

mcall.ncon.gwm.df
```

##### Plot groupwise means
```{r}
mcall.ncon.gwm.df %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = Mean,
                       group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean cumulative nectar consumption") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(mcall.fcon.gwm.df$fd_day))
```


##### Model diagnostics 
```{r}
plotNormalHistogram(residuals(mcall.ncon.model.1))
plot(residuals(mcall.ncon.model.1),
     fitted(mcall.ncon.model.1))
plot(mcall.ncon.model.1)
plot(residuals(mcall.ncon.model.1))
acf(residuals(mcall.ncon.model.1))
```


##### Plotting raw summarised
```{r}
mc.feed.all.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(total_p_cons = cumsum(p_mass_cons_avg),
         total_n_cons = cumsum(n_mass_cons)) %>%
  group_by(fd_day, treatment) %>%
  summarise(nectar_cons = mean(total_n_cons), 
            nectar_se = (sd(total_n_cons) / (sqrt(n()))), 
            pollen_cons = mean(total_p_cons, na.rm = TRUE), 
            pollen_se = (sd(total_p_cons, na.rm = TRUE) / (sqrt(n())))) %>%
  filter(fd_day != 0) %>%
  ggplot() +
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_pointrange(mapping = aes(x = fd_day,
                                y = nectar_cons,
                                ymin = nectar_cons - nectar_se,
                                ymax = nectar_cons + nectar_se,
                                color = treatment),
                  size = 1.0) +
  geom_smooth(mapping = aes(x = fd_day,
                            y = nectar_cons,
                            color = treatment), 
              se = FALSE,
              size = 1.5) + 
  theme_microcol() + 
  ylab("Mean nectar consumption") + 
  xlab("Interval Feeding Day") + 
  scale_color_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.position = "nothing") + 
  scale_x_continuous(breaks = unique(mc.feed.all.df$fd_day)) + 
  ggsave("ncons.eps", width = 7, height = 3.5)
  
```

```{r}
mc.feed.all.df %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(total_p_cons = cumsum(p_mass_cons_avg),
         total_n_cons = cumsum(n_mass_cons)) %>%
  group_by(fd_day, treatment) %>%
  summarise(nectar_cons = mean(total_n_cons), 
            nectar_se = (sd(total_n_cons) / (sqrt(n()))), 
            pollen_cons = mean(total_p_cons, na.rm = TRUE), 
            pollen_se = (sd(total_p_cons, na.rm = TRUE) / (sqrt(n())))) %>%
  filter(fd_day != 0) %>%
  ggplot() +
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_pointrange(mapping = aes(x = fd_day,
                                y = pollen_cons,
                                ymin = pollen_cons - pollen_se,
                                ymax = pollen_cons + pollen_se,
                                color = treatment),
                  size = 1.0) +
  geom_smooth(mapping = aes(x = fd_day,
                            y = pollen_cons,
                            color = treatment), 
              se = FALSE,
              size = 1.5) + 
  theme_microcol() + 
  ylab("Mean nectar consumption") + 
  xlab("Interval Feeding Day") + 
  scale_color_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.position = "nothing") + 
  scale_x_continuous(breaks = unique(mc.feed.all.df$fd_day)) + 
  ggsave("pcons.eps", width = 7, height = 3.5)
  
```

## LMM Total P/N consumption
#### Gather data
```{r}
mc.all.npcons.df <- mc.feed.all.df %>%
  ungroup() %>%
  group_by(id, treatment, rep) %>%
  summarise(total_p_cons = sum(p_mass_cons_avg),
            total_n_cons = sum(n_mass_cons))
```

#### Pollen
##### Model specification/diagnostics
```{r}
mcall.pcons.lmm <- lme(total_p_cons ~ treatment + rep,
                       random = ~ 1 | id,
                       data = mc.all.npcons.df,
                       na.action = na.exclude)

tidy(mcall.pcons.lmm)
summary(mcall.pcons.lmm)
anova(mcall.pcons.lmm)

plotNormalHistogram(residuals(mcall.pcons.lmm))
plot(residuals(mcall.pcons.lmm),
     fitted(mcall.pcons.lmm))
plotNormalHistogram(mc.all.npcons.df$total_p_cons)
```

##### LS means Calculation
```{r}
mcall.pcons.marginal <- lsmeans(mcall.pcons.lmm, ~ treatment)
mcall.pcons.cld <- cld(mcall.pcons.marginal,
                       alpha = 0.05,
                       Letters = letters,
                       adjust = "tukey")
mcall.pcons.cld
```

##### Plot LS means
```{r}
mcall.pcons.cld$.group=gsub(" ", "", mcall.pcons.cld$.group)
ggplot(data = mcall.pcons.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 1),
             color = "black") + 
  scale_y_continuous(limits = c(0, 20),
                     expand = c(0, 0)) +
  ylab("Least square mean total pollen consumption (grams)") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

#### Nectar
##### Model specification/diagnostics
```{r}
mcall.ncons.lmm <- lme(total_n_cons ~ treatment + rep,
                       random = ~ 1 | id,
                       data = mc.all.npcons.df,
                       na.action = na.exclude)

tidy(mcall.ncons.lmm)
summary(mcall.ncons.lmm)
anova(mcall.ncons.lmm)

plotNormalHistogram(residuals(mcall.ncons.lmm))
plot(residuals(mcall.ncons.lmm),
     fitted(mcall.ncons.lmm))
plotNormalHistogram(mc.all.npcons.df$total_n_cons)
```

##### LS means Calculation
```{r}
mcall.ncons.marginal <- lsmeans(mcall.ncons.lmm, ~ treatment)
mcall.ncons.cld <- cld(mcall.ncons.marginal,
                       alpha = 0.05,
                       Letters = letters,
                       adjust = "tukey")
mcall.ncons.cld
```

##### Plot LS means
```{r}
mcall.ncons.cld$.group=gsub(" ", "", mcall.ncons.cld$.group)
ggplot(data = mcall.ncons.cld,
       mapping = aes(x = treatment,
                     y = lsmean,
                     label = .group)) + 
  geom_col(mapping = aes(fill = treatment),
           width = 0.35,
           alpha = 1,
           color = "gray10") + 
  geom_pointrange(mapping = aes(ymin = lower.CL,
                                ymax = upper.CL),
                  color = "black") + 
  theme_microcol() + 
  theme(legend.position = "right") +
  geom_text(mapping = aes(y = upper.CL + 5),
            color = "black") + 
  scale_y_continuous(limits = c(0, 150),
                     expand = c(0, 0)) +
  ylab("Least square mean total nectar consumption (grams)") + 
  xlab("Treatment") + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(1, 1), 
        legend.position = c(1, 1))
```

## RM ANOVA on avg daily worker mortality
This is average daily worker mortaility, not cumulative.  See next section for cumulative worker mortality (similar to RM ANOVA for drone production) 
#### Gather data
```{r}
mc.all.work.df <- bind_rows(
  select(mc1.df, 
         id, 
         treatment, 
         date, 
         n_worker_deaths, 
         fd_day),
  select(mc2.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day), 
  select(mc3.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day),
  .id = "rep")
```

#### Temporal correlation structure
```{r}
mcall.work.model = lme(n_worker_deaths ~ treatment + rep + date + treatment*date, 
                       random = ~ 1 | id,
                       data = mc.all.work.df,
                       na.action = na.exclude)

ACF(mcall.work.model) # 1st order lag: 0.8272
```

#### Full model
```{r}
mcall.work.model.1 = lme(n_worker_deaths ~ treatment + rep + date + treatment*date, 
                         random = ~ 1 | id,
                         data = mc.all.work.df,
                         correlation = corAR1(form = ~ date | id,
                                              value = 0.1708),
                         na.action = na.exclude,
                         method = "REML")
Anova(mcall.work.model.1)
summary(mcall.work.model.1)
anova(mcall.work.model.1)
tidy(mcall.work.model.1)
```

#### Groupwise means
```{r}
mcall.work.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  n_worker_deaths ~ treatment + fd_day,
  data = mc.all.work.df,
  conf = 0.95,
  digits = 3
  )

mcall.work.gwm.df
```

#### Plot groupwise means
```{r}
mcall.work.gwm.df %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = Mean,
                       group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean daily worker deaths") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(mcall.work.gwm.df$fd_day))
```

#### Model diagnostics 
```{r}
plotNormalHistogram(residuals(mcall.work.model.1))
plot(residuals(mcall.work.model.1),
     fitted(mcall.work.model.1))
plot(mcall.work.model.1)
plot(residuals(mcall.work.model.1))
acf(residuals(mcall.work.model.1))
```

## RM ANOVA on cumulative daily worker mortality
#### Gather data
```{r}
mc.all.work.df <- bind_rows(
  select(mc1.df, 
         id, 
         treatment, 
         date, 
         n_worker_deaths, 
         fd_day),
  select(mc2.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day), 
  select(mc3.df,
         id,
         treatment,
         date,
         n_worker_deaths,
         fd_day),
  .id = "rep")
mc.all.work.df <- mc.all.work.df %>%
  filter(!is.na(n_worker_deaths)) %>%
  mutate(cum_worker_deaths = cumsum(n_worker_deaths))
```

#### Temporal correlation structure
```{r}
mcall.cumwork.model = lme(cum_worker_deaths ~ treatment + rep + date + treatment*date, 
                          random = ~ 1 | id,
                          data = mc.all.work.df,
                          na.action = na.exclude)

ACF(mcall.cumwork.model) # 1st order lag: 0.8272
```

#### Full model
```{r}
mcall.cumwork.model.1 = lme(cum_worker_deaths ~ treatment + rep + date + treatment*date, 
                            random = ~ 1 | id,
                            data = mc.all.work.df,
                            correlation = corAR1(form = ~ date | id,
                                                value = 0.9492),
                            na.action = na.exclude,
                            method = "REML")
Anova(mcall.cumwork.model.1)
summary(mcall.cumwork.model.1)
anova(mcall.cumwork.model.1)
tidy(mcall.cumwork.model.1)
```

#### Groupwise means
```{r}
mcall.cumwork.gwm.df <- groupwiseMean( # This cannot have missing values for mean to be calc'd
  cum_worker_deaths ~ treatment + fd_day,
  data = mc.all.work.df,
  conf = 0.95,
  digits = 3
  )

mcall.cumwork.gwm.df
```

#### Plot groupwise means
```{r}
mcall.cumwork.gwm.df %>%
  mutate(trt_cat = ifelse(treatment == "zone.1", 
                          "constant", 
                          ifelse(treatment == "zone.2", 
                                 "constant", 
                                 "pulse"))) %>%
  ggplot(mapping = aes(x = fd_day,
                       y = Mean,
                       group = treatment)) + 
  annotate("rect",
           xmin = 3.5,
           xmax = 6.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  annotate("rect",
           xmin = 10.5,
           xmax = 13.5,
           ymin = -Inf,
           ymax = Inf,
           fill = "black",
           alpha = 1) +
  geom_errorbar(
    mapping = aes(ymin = Trad.lower,
                  ymax = Trad.upper),
    width = 0,
    size = 0.7,
    #position = position_dodge(0.2),
    color = "black") + 
  geom_point(mapping = aes(color = treatment),
             size = 4,
             #position = position_dodge(0.2),
             alpha = 1) + 
  geom_line(mapping = aes(color = treatment),
            alpha = 1,
            size = 1.5) +
  # geom_smooth(mapping = aes(color = treatment),
  #             alpha = 0.5,
  #             size = 2.0,
  #             se = FALSE,
  #             span = 0.6) + 
  theme_microcol() + 
  scale_color_manual(values = c("#9FC3EA", 
                                "#172A3A", 
                                "#E6AF2E",
                                "#F3E37C"),
                     labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1)) + 
  facet_grid(rows = vars(trt_cat)) + 
  ylab("Least square mean cumulative worker deaths") +
  xlab("Interval Feeding Day") + 
  scale_x_continuous(breaks = unique(mcall.work.gwm.df$fd_day))
```

#### Model diagnostics
```{r}
plotNormalHistogram(residuals(mcall.cumwork.model.1))
plot(residuals(mcall.cumwork.model.1),
     fitted(mcall.cumwork.model.1))
plot(mcall.cumwork.model.1)
plot(residuals(mcall.cumwork.model.1))
acf(residuals(mcall.cumwork.model.1))
```

## Growth periods 
```{r}
mc.feed.all.df %>%
  ungroup() %>%
  ggplot() + 
  geom_point(mapping = aes(x = fd_day,
                           y = mc_mass_true,
                           color = pulse_cat)) + 
  geom_smooth(mapping = aes(x = fd_day,
                            y = mc_mass_true_intrp,
                            color = pulse_cat),
              method = "lm",
              se = FALSE) + 
  scale_x_continuous(breaks = unique(mc.feed.all.df$fd_day)) + 
  theme_microcol() + 
  facet_grid(vars(treatment)) + 
  ggsave("periodgrowthraw.eps")
  
```

```{r}
trt.slopes <- function() {
  trts <- unique(mc.feed.all.df$treatment)
  df.ls <- list() 
  for (i in trts) {
    df <- mc.feed.all.df %>%
      filter(treatment == i) %>%
      plyr::dlply("pulse_cat", function(.)
        tidy(lm(mc_mass_true ~ fd_day, data = .))) %>%
      bind_rows(.id = "id") %>%
      mutate(treatment = i)
    df.ls[[i]] <- df
  }
  df.end <- bind_rows(df.ls)
  assign("mc.all.trtslope.df",
         df.end,
         envir = .GlobalEnv)
}
trt.slopes()

```

```{r}
mc.all.trtslope.df$id <- as.factor(mc1.trtslope.df$id)
mc.all.trtslope.df$id <- factor(mc1.trtslope.df$id, levels = c("b1",
                                                            "p1",
                                                            "a1.b2",
                                                            "p2",
                                                            "a2"))
mc.all.trtslope.df %>%
  filter(term != "(Intercept)") %>%
  ggplot() + 
  geom_pointrange(mapping = aes(x = id,
                                y = estimate,
                                ymin = estimate - std.error,
                                ymax = estimate + std.error,
                                color = treatment),
                  size = 1) +
  geom_line(mapping = aes(x = id,
                           y = estimate,
                           group = treatment,
                           color = treatment),
            size = 1.25,
            alpha = 1) + 
  geom_hline(yintercept = 0,
             color = "tomato2",
             size = 1,
             alpha = 1) + 
  labs(x = "Period relative to food pulse",
       y = "Estimated rate of mass gain") + 
  scale_y_continuous(limits = c(-3.25, 3.25),
                     breaks = seq(-3, 3, by = 1)) + 
  theme_microcol() + 
  scale_fill_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment") + 
  scale_color_manual(values = c("#9FC3EA", 
                               "#172A3A", 
                               "#E6AF2E",
                               "#F3E37C"),
                    labels = c("50% - Constant",
                               "100% - Constant",
                               "100% - Variable",
                               "50% - Variable"),
                    name = "Treatment")
```

